\documentclass[char]{airship}
\begin{document}

\name{\cCid{}}

\cenquote{``If I cannot swear in heaven, I shall not stay.''}{Samuel Clemens} 

You were born Abigail, daughter of Lord and Lady \cNoble{\first\ 
\middle\ \last}. Both your parents are strict traditionalists -
probably on account of your family's substantial inherited fortune and
lavish titles. Your father is tolerable despite his stodgy ways. Your
mother is a raving bitch spawned in the pits of hell. When you were
younger - maybe 12 - your eldest brother, Augustine, committed
suicide. You didn't get it then. Your mother just told you that
Augustine was gone, and refused to speak of him ever again. By the
time Thomas left, you understood. She was insane. Religion was her
only obsession. Nothing, no-one was free of sin. She forced Thomas to
pray for penance for going by "Tom" instead of "Thomas Aquinas" for
God's sake! Of course, when Tom was gone, she turned her sights to you
and made your life a living hell. Nothing you did pleased the Lord, or
her. You were wicked, sinful, disgusting. You didn't respect the
sabbath, or properly honor her, or respect your place as a woman, a
temple of purity to God Almigty.

What a bitch.

You found a bit of an escape in tinkering.  Take a gadget apart, put
it back together. Break it, then fix it. Eventually, you bribed your
father's mechanic into teaching you what he knew. He was shocked that
a \emph{girl} was such a quick study, and so were you, frankly. Before
you learned it was best to hide your hobby from your parents, they had
made it very, very clear that it Was Not Proper for a woman to want to
learn something as impractical as how a contraption worked. As if she
would ever need to know that!

But you couldn't help it. Machines were \emph{interesting}. You kept
at it, and of course you got caught a few times. Your father
eventually gave a little. It was alright for a young lady to have a
hobby, as long as she was discreet. And, of course, all this nonsense
would go when you were wed. Your mother, though, was something else
entirely. She seemed to take the whole bloody thing personally. It
wasn't that your interests were unusual, it was that you were trying
to subvert the social order in the Major household and all of
the endless work she had poured into you and your sibling's
upbringing. You weren't just shaming your family, you were shaming
{\em her}, in the eyes of her peers and the Lord. You were sullying yourself
before God. To listen to her rants, every damn time you touched a
screwdriver, you were cutting her open and pouring her guts all over
the floor.

Faced with all that, you did what you were told, for the most part,
all the while a little knot of resentment growing inside you. And then
it all 'pinged' right into place. \emph{You keep this up, you're
ending up just like your mother.} Bitter, nothing left of your dreams,
just the society that squelched them, so you'll cling to that
instead. Probably would mother just like her, too. Killing your
children inch by insane, ranting inch. That night, you grabbed a
traveling bag, filched a few sets of the servants' clothing, cut your
hair with a knife from the kitchen, and stole the mechanic's tools
before running off with a good chunk of cash. No way in the goddamn
hells were you turning into a raging bitch like her. Someone out there
had to need a good mechanic.

Someone turned out to be a garage formed by a couple engineers who
wanted a third hand around the shop. They were crude, rowdy,
foul-mouthed, and drunk half the time, but they respected your
talent. They had a wealth of knowledge that they were eager to share,
and you count those few years among the best of your (admittedly
incomplete) life. Of course, you picked up a few habits along the
way. Cursing and drinking like a veteran soldier definitely helped
your disguise, but you'd be lying if you said you didn't enjoy it, at
least a little. In fact, as time passed, being 'Sid' was less an act,
and more ... just you. It wasn't a bad change at all, you decided. You
were loud, but at least you got heard, and you could back up your
swagger. So what if everyone you knew in the old days would sniff and
call your behavior 'vulgar' or 'uncivilized'? You were free, and
nobody who mattered now would give a damn.

Well, almost nobody. One minor exception would be \cCurie{\intro}, an
official of Her Majesty's Engineering Corps - and publically female to
boot. You two butted heads at a conference of sorts, first arguing
over theories, but drifting somewhere in the debate to personal
attacks. You're pretty sure she started in on the accusations of being
'a disgusting, violent carouser', 'an example of the worst that men
could sink to', and 'an ignorant chauvinist' before you responded with
'shrieking paranoid bitch' and 'dried up hag who thinks she's found
the key to a life of virtue, health, and a goddamn spitting pedestal
to hawk onto all of us below.' Of course, you realize now that you
were projecting not a little of your mother onto her, but given how
she tore into you, you wouldn't be surprised if she had a special hated
someone of her own. That initial disagreement has evolved into
something of a grudge or a rivalry - a few heated exchanges in public,
lots of arguing through mutual contacts, some editorial arguments in a
trade newsletter. It's a damn shame, really. Perhaps if you'd not been
disguised as a man, she'd be a colleague instead of a rival. But
there'd still be some of her more crackpot works to contend with then,
so perhaps not.

   
A few weeks after your first shouting match with \cCurie{}, a Mr. John
Archer dropped by the shop. He turned out to be an ex-soldier too, an
airship captain that your mentors had served with. He was looking for
an engineer to crew a ship he was building - and although Rich and
Mike both swore they'd have nothing to do with airships ever, ever
again after the war, the next thing out of their mouths was, ``Give us
a bit to show Sidney how its done, and you'll have the best damn
engineer you could want.''

Working on an airship - a \emph{real} airship, innovative in design,
made to be the best in the sky, was like discovering machines all over
again. You'd sometimes spend days at a time, putting her inner
workings together piece by piece, getting to know her better than your
own home. You've learnt every rattle and wheeze the engine can throw
out in ground testing, what it means, how to fix it.

And hell, not to get too misty-eyed, but you might have found yourself
a bit of a family, too. Well, nowhere as strong as blood ties, of
course, but people who you know well, a place where you belong. A
definite step up from the hellhole your mother still
tyrannizes. \cRobot{} was hired as an assistant for you early on in
the construction - originally he was just for hauling bolts and
shoveling coal, but \cRobot{} was insatiably curious, and smart enough
to take in all the answers you gave him. He's oddly perceptive about
somethings - he is the only one who has noticed your true gender. You
have told him not to tell anyone. He doesn't seem to understand why
you must keep it secret. Such a strange, interesting boy. You're
planning to take him on as an apprentice - he certainly enjoys working
on the ship and teaching such a bright lad would be a pleasure. He is
very naive about the world, and does understand other people very
well. He looks up to you quite a lot, and you must confess you enjoy
the attention and have found yourself with almost motherly feelings
towards him. The daughter of the Captain, \cThief{}, regularly visits
the the construction site, with the blessings of her father. Lucky
girl. She was refreshing company during your breaks, after a few years
of your boisterous peers, but adventurous and lively enough that she
wasn't boring. She liked your company, too - perhaps a bit too well,
given that she \emph{kissed} you in a stairwell recently. You jumped
high enough to hit your head on a pipe, and then tumbled down the
stairs while \cThief{} giggled, out of nervousness, or amusement, or
insanity: you don't really know. Crazy girl. You're not quite sure
what to do about this, besides avoid the subject entirely. Just
because you've pretended to be a man for the last few years doesn't
mean you've turned into one.

But that's just a little added worry. Tonight is the big night.  Now is not the time to fret about your secret identity, about \cThief{}, about your parents, of all people, being on the guest list. Tonight is the start of your life as the best engineer in England on the finest machine devised by man. The maiden flight of \emph{The Dauntless}.


%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Keep your cover intact. Although it's second nature to you now, one little slip could destroy your whole life. 
  \item Keep the ship flying!
  \item \cRobot{}'s got a good head for machines - do your best to turn that spark into a fire and make him a great mechanic.
  \item As much as you hate to admit it: Seeing your parents has made you realize how much you miss them. Well. How much you miss your father, at least. Maybe you could just talk with him discreetly?
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cCaptain{}} - Captain of the \emph{HMS Dauntless}, and your current employer.
  \contact{\cRobot{}} - Your assistant and coal-shoveler. A surprisingly sharp boy.
  \contact{\cNoble{}} - Your father, who you haven't seen in quite some time.
  \contact{\cJack{}} - Pleasant as a shark with a spike up its ass, but your mother all the same. Unfortunate, that.
  \contact{\cVicar{}} - Brother of the captain, stern religious type. You've only seen him once or twice.
  \contact{\cCowboy{}} - His legs are what looks like a Yankee knock-off of the Galatea Mk II prosthesis. Modified a bit, too, if you're not mistaken. A friend of the Vicar's. 
  \contact{\cThief{}} - Daughter of the captain. The flirting has turned your friendship with her all kinds of awkward {\ldots}
  \contact{\cCurie{}} - What a terrible woman. Don't let her upstage you.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
  \memfold{Open at game start.}{{\emph{Massive explosions rock the ship.}} Sweet whore-humping son of God! Sounded like more than one blast, too - time to get to work.}

\memenvelope{ Item \# 645}{...That's a bomb, alright. \emph{The enclosed notebook is now yours. Open the first page.}}

\endtag

\starttag{abils}
  \ability{Disguise}{You are actually female. You must display your ``Abigail'' namebadge to anyone who sees you unclothed, or performs an invasive search. You may also switch your namebadges at will.}{I'm actually female! {\it I look like badge number \#230}}
\endtag


\end{document}
