\documentclass[char]{airship}
\begin{document}

\name{\cCowboy{}}


\bigquote{``In war, a man does not have to be killed or wounded to become a casualty.  His life, his sight, or limbs are not the only things he stands to lose.''}{-- Philip Caputo}


It was on July 16 that you lost your faith.  All your life, you prayed
to God like Mom and Pop taught you.  Even when you were out on the
plains, running supply lines and escorting cargo cross Texas, every
Sunday you got down on your knees and prayed like you were in Church
listening to the Preacher, just like you did when you were a little
boy.  No one gave you any trouble for it, either.  No, holding onto
that faith like you did was a wonder out there.  Made you more of a
man, someone the younger boys could look up to.  They said you'd
probably be a preacher if you didn't love the job so much.

Until the Incident, that is.

It was supposed to be a routine transport.  The folks down in the CSA
wanted some of the new toys the engineers up in the USA had cooked up.
So, just like every other time, the imports came down through the way
of Texas.  Transport with you as the middleman always ended with a
pretty penny for you, so of course you took the job.  Take the crates
across the plains, drop it off in Louisiana, get paid.

Except, of  course, that  didn't happen.  It  was getting  hot, hotter
than it  had been  in years  previous.  You were  riding close  to the
transport, hoping to  get at least some margin of  shade.  No one told
you  that  the  assholes   who  ordered  the  stuff  actually  ordered
explosives.  No, they wanted it to be hushed up.  The goddamned idiots
never  told you  that you  were carrying  explosives through  a desert
during  record highs,  because they  couldn't be  bothered to  pay the
extra it would have cost to do the job safely.

You lost both your legs in the explosion.  God wasn't there to save
you from the fire, from the shrapnel, from the pain.  You had lived
your life like how you were told God wanted you to, and where was He
when you needed him the most?  If He existed, He was off somewhere the
hell else, that's for sure.  He apparently didn't give a damn about
you.  And if He couldn't be bothered to give a damn about you, you
sure as hell wouldn't be bothered to give a damn about Him either.

You were eighteen years old.

When the engineers who had sold the explosives found out about, they
were horrified.  Transported your broken self up to their hospitals
and did their best to repair the damage.  The docs up North gave you
mechanical legs devised by one of the engineers to replace the ones
you'd lost.  They didn't take any money either.  Guilt, you guess.  In
any case, they fixed you up as best they could.

It just wasn't the same, though.  Although you could walk, even run,
with your new legs, you couldn't ride a horse.  And if you couldn't
ride a horse, then your days as a transport escort were over.  Which
effectively meant that what you've depended on for your funds was
gone.

But you're not the type of person who'll take this kind of thing lying
down, no sir.  Since you couldn't work, you decided to figure out who
the son of a bitch responsible for ruining your life was.  Using what
little contacts you had and just plain old fashioned stubborness, you
eventually got a lead on who originally bought those explosives.
Turns out that there was an cute little paper trail that led you
straight to some Brit named \cDealer{\intro}, who not only meddles in CSA
politcs, but has some sketchy dealings with the underworld to boot.
Having this information, the only thing stopping you from getting your
revenge was a rather large body of water known as the Atlantic Ocean.

Luckily, as you were hunting down all this information, you ran into a
British clergyman by the name of \cVicar{\intro}, who has apparently made
it some kind of mission of his to ``bring you back to the Flock''.
Whatever.  He's a good man, in any case, and really doesn't prostylize
too much.  In fact, you rather enjoy the theological and ethical
discussions the two of you get into.  He managed to get you a few
books from England that have recently become rather popular.  Your
favorite, by far, is the translation of ``Ragnarok'' by
\cSaboteur{\intro}.  There's a message in there, hidden, that speaks to
your sensibilites.  You really like his work, in any case, and it
makes for great material to fuel your discussions with the good Vicar.

In any case, the good Vicar has decided to return to England and has
graciously offered to bring you along.  Of course you jumped at the
chance.  Once in London, you managed to do a little more information
gathering and managed to track down this {\cDealer{}}.  It was night
and you managed to track him to one of his transactions.  Apparently,
not only does he have sketchy connections to the underworld, but he's
a damned opium dealer to boot.  Unfortunately, he heard you coming on
your blasted legs.  Tried to shoot you in the legs a few times before
getting away.  At least they're good for something.  Except, the shots
got lucky and damaged some parts of your legs.  Now they're not
working quite right, and you have no idea where you're going to get
the parts or find someone competent enough to fix them.

You're currently staying with the Vicar, who, in an effort to cheer
you up and take your mind off your problematic legs, has invited you
on his brother's new airship, the HMS Dauntless, for her maiden voyage
on New Year's Eve. You have plans for the flight, you
see. Particularly this South African diamonds letter you recently
received.  You're not sure if you take it seriously, but if everybody
else is, you're certainly not going to let some London mafioso get his
dirty hands on it.

So here you are, on an airship going from London to Paris.  You
managed to get a copy of the passenger list prior to boarding. To your
great joy, \cSaboteur{\intro} will be here. You can't wait to meet him and
converse with him. Even better, though is another listed guest:
{\cDealer{\intro}}.

Revenge is the perfect way to ring in a new year, isn't it?

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Fix your rusted body.
  \item Secure the contract for the South African diamond company for America.  You've got some contacts who'd be mighty interested in that.
  \item Find evidence that Bryce is a criminal, and then neutralize him.
\end{itemz}

\begin{itemz}[Notes]
  \item The lower two-fifths of you is made of heavy, lumbering metal. Roleplay accordingly.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cVicar{}} A man of the cloth, who has helped you out on more than one occasion, despite your ideological differences.
  \contact{\cDealer{}} Son of bitch is the guy responsible for blowing your legs up.  You want revenge, and he's not getting away this time.
  \contact{\cSaboteur{}} A writer.  You read his novel ``Ragnarok'' in translation, and found it absolutely brilliant, especially all the hidden messages.
  \contact{\cThief{}} The vicar's very charming young niece.
  \contact{\cCaptain{}} The vicar's brother, and \cThief{}'s father.
  \contact{\cBoddy{}} The man you are to meet.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
%%  \mTest{}
  \memfold{Open at game start.}{A series of explosions rock the ship! You are thrown to your already aching knees. What the hell kind of voyage is this?}
  \memfold{Open if your $\chi$ is 6.}{You see the light! How could you ever have forsaken God? \cVicar{\intro} was right all along! You are seriously considering converting back to Christianity. Destroy your ``Open if your $\chi$ is -6'' mempack. Roleplay accordingly.}
  \memfold{Open if your $\chi$ is -6.}{You see the light! How could you have ignored the class struggle for so long? \cSaboteur{\intro} was right all along! You're seriously considering dedicating yourself to her cause and asking her how you can help. Destroy your ``Open if your $\chi$ is 6'' mempack. Roleplay accordingly.}
  \memfold{If you fix your Right Calf}{You may walk and attack normally.}
  \memfold{If you fix your Left Ankle}{Your CR increases to 2.}
  \memfold{If you fix your Left Knee}{Your CR increases to 3. Tear up your ``\aCripple{}'' ability.}
\endtag


\end{document}
