%%%%%

\documentclass[char]{airship}
\begin{document}

\name{\cDealer{}}


\cenquote{``You play your cards so close to your chest, that I'm not sure that they're really cards at all.''}{-- Neil Gaiman, American Gods}

Your uncle had warned you that this would happen someday.  ``There
comes a time in a man's life where the chance to be something great
appears in front of him.  The trick is to know when that moment comes
and grab hold of it and run,'' he'd say to you, when you were a young
boy sitting on his lap as he worked the books.

You were born in Aberdyfi, Wales, the second son of the village
tailor.  Your elder brother, Owen, was the one to inherit your
father's business, which left you with little options in what to do.
So when your Uncle Bran, a merchant, offered to take you under his
wing, you jumped at the chance to escape a life in a little
sheep-herding village.  Your father, knowing that your spirit yearned
for the bigger world, gave Bran his blessing in teaching you a
merchant's trade, and you left home at the age of ten.

However, what your father didn't know, and you're fairly certain he
would never had let you go if he had, was Uncle Bran's connections to
a less-than-savory business world.  While he did own and operate a
rather successful silk and tea shipping fleet to the eastern colonies,
his more lucrative business ventures involved the transport of a far
more illegal substance: opium.  So, at the tender age of ten, you were
introduced to the fiscal, poltical, and territorial battleground known
as the international underground.  At your uncle's knee, you learned
the tricks of the trade, from money laundering and creative accounting
to knife fighting to smuggling.  You grew up in two worlds, one as the
apprentice of a respected cloth merchant and one as the nephew and
heir of the boss of one of the largest opium rings in the British
Empire.

To complete the image of respectibily, Uncle Bran made sure you
recieved the best education money could buy in the form of private
tutors (who knew of Bran's ties to the underworld and were trusted
members of the organization, of course) in every subject a respectable
young man should have a firm grasp in.  You learned your lessons well.
When you were twelve, some men hired by Bran's rivals cornered you
while you were closing up the shop for the day.  They wanted to send a
message to your uncle in the most brutal way possible, which probably
involved your corpse showing up on his doorstep.  Unfortunately for
them, you had paid attention during your daily lessons in combat just
as much as you did during all your other lesssons.

You were a very studious child.

Bran found you sitting in the shop when you didn't come home right
away, two bodies in a nearby alleyway and your knife, still bloody,
laying at your feet.  He said nothing, only picked up the knife and
cleaned it before holding it out to you.  When you didn't take it
back, he picked you up and carried you home.  You still remember that
night, sitting on his lap by the fire, not trying to make light of the
fact that you had killed two men, but that it had been neccessary for
your survival, that he had been only a few years older than you when
he had been forced to kill for the first time.  It was at that moment
you realized why his rivals had tried to attack you to harm him: you
were his heir, and more than that, you were like the son he never had.
You understood why he had taken you away from Aberdyfi in the first
place, because he saw himself in you.

After that, Bran kept you at his side as much as he was able.  You went to meetings with smugglers and helped arrage deals on opium prices.  You started managing the books of both the cloth and opium enterprises.  You still remember Uncle Bran's look of absolute shock when you brought in a plan of how to increase profits by 8\% simply by reorganizing the budget and keeping better track of where some of the expenses went.  He took one look at it, declared you a genius, and implemeted it right away.  At the age of sixteen, he placed you in charge of managing local operations.  You gained a reputation in circles as someone not to be taken lightly, and earned the respect of those under your uncle who now reported to you despite your age.

That respect proved useful when you were nineteen.  Bran had gone out on one of his ``business trips'', leaving you in charge.  When he was two days late with no word as to why, you knew something had gone wrong.  The next day, one of the men who had gone with your uncle staggered into the shop, dirty, exhausted, and clutching his left arm, which was flaked with dried blood.   The deal had gone sour.  Bran had tried to be a reasonable man, but the other men would not see reason.  The man standing in your shop had been ordered by your uncle to get away and bring word to you.  The following day, a copper appeared on your doorstep.  Bran Bryce had been found floating face-down in a river, with several stab wounds.  Following the funeral, you took over both enterprises fully, as Bran had left everything he owned to you.  There had been some initial grumbling, but any resistance to your authority was quickly stamped out by yourself and those whose respect you had earned.

Overall, things went smoothly for the next few years, other than the clashes and turf wars between rival rings that had become boringly mundane to you.  You knew exactly how to manipulate people for the most favorable outcome for yourself and your businesses, which is why you were so damned good at what you do.  In some ways, it was like a game to you.  You were one of the most powerful men in the underworld, but the picture of respectibilty in more legit circles.  You can wine and dine all the movers and shakers, maneuver with the best of them, and read all the right books, even ones on the cutting edge.  One recent book you've read was the international bestseller by \cSaboteur{\intro}.  Originally, you picked up for some light reading (and for social conversation), but as you read it, you started seeing what the book was \textit{really} talking about: classes in society.  Well.  You know all about \textbf{that}.  But what a novel and interesting way to discuss what really goes on with the lower classes!  Why, it goes right under the noses of the nobility.  Of course, you, with a foot in both worlds, could work these ideas to your advantage.  And did you ever.  Despite your humble origins in the Welsh countryside (which some fools still brought up to try to make you look inferior), your money allowed you access to the circles frequented by nobility and a place among them.

It was at one such gathering that you were introduced to a vision of
beauty that haunts you still.  Her name is \cThief{\intro}, and a finer
example of the fairer sex you have never laid eyes upon.  Like most of
the young women you have met in these circles, she is all that a lady
of her social standing should be: refined, graceful, and charming to
the utmost degree.  But what set \cThief{} apart from the rest was the
spark in her eyes, a sense of life and spunk that was missing from all
the others.  There is something about her that seems to be just
lurking beneath the surface, and that something draws you to her like
a moth to light.

Except, she's the daughter of \cCaptain{\intro}, one of the most respected
veterans of the Steam War and a noble to boot.  The only way to win
her hand is to be exactly the kind of man her intimidating father
would want for his only daughter, which means you are using every
trick in the book to appear as the most charming, refined, polite,
genteel young man any father could ask for.  Above all else, for God's
sake, he {\em must not} find out about your opium ring!  You have
enough trouble with having appeared to have earned your money with the
cloth and tea trade; there would be no chance in hell if \cCaptain{}
found out a crime boss wanted to marry his daughter.

And \cNPCWhore{\intro} is with you. A whore you hired last night who decided
to stick around.  You put her on the guest list for now, but really
you just want her gone so you can concentrate on \cThief{}. You've
been passing her off as your sister - even got her on the guest list
at the last minute.

In addition to playing a potentially dangerous game in social circles,
there might be some trouble brewing in the underworld.  You think it
might be one of your rivals trying to bring you down, but in any case,
you aren't happy about it.  It happened a few weeks ago.  You were
making a routine check of a few warehouses, touching base with your
managers and catching up with some of the workers, when out of nowhere
you hear this steady clanking, like metal hitting the dock.  You turn
around and there's this man screaming at you as he charges at you
wielding a gun.  You've never managed to forget your training, and so
on reflex, you pull out your own gun and fire off a few shots at his
legs.  You didn't want to kill him before you got some answers, so you
were aiming to disable him.  To your amazement, the shots ricocheted
off.  You aren't an idiot, so when you saw that your shots did
nothing, you ran.  (Thankfully, for the sake of your business, your
managers and men got the right idea and fled as well) From the accent
you caught from the obscenities he yelled at you, you're guessing he's
an American.  Figures it would be someone so uncultured.  But why the
hell would an American be sent after you?  It doesn't make any sense.
Perhaps it might be a good idea to find someone to start training as
an apprentice, just in case.  Uncle Bran always extolled the virtue of
anticipation.  If someone's out to get you, make it out alive and make
sure that your business doesn't get hurt.  There are a lot of good men
working for you, and the last thing they deserve is someone ruining
their lives because they don't care.

In addition to worrying about some bloody American trying to kill you,
you've gotten some intel from some very reliable sources about a bit
of a business opportunity that's cropped up.  Someone is attempting to get at the diamonds in South Africa, and this time, they seem to have a plan of how to make it work.  If you could get your hands on a
claim to it, this could be the biggest thing that happened to your
opium ring since the invention of the airship.  Just as important is a
recent deal you've made with \cBoddy{}: only the biggest, and most
dangerous, opium run you've ever done.  A shipment of opium from
London to Paris, smuggled onboard (courtesy of \cBoddy{}, who'll let
you know where it is after takeoff) the luxury airship {\it HMS
Dauntless} on it's maiden voyage.  Not only is this being done on a
high-profile airship, but on the airship captained by \cCaptain{} no
less!

There are so many things that can possibly go wrong, but you're always
up for a challenge.  So it's going to take all of your considerable
skill and knowledge, not to mention every trick in the book, to pull
this off successfully {\em and} not destroy everything both Bran Bryce
and yourself have worked towards.  {\cDealer{}} is going to be a name
that will be respected throughout the international underworld, and
you can think of no finer way to do it than this.

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Make sure the opium shipment gets to Paris safely, by meeting with Blackwell.
  \item Try to win {\cThief{}}'s hand and her father, {\cCaptain{}}'s approval.
  \item Secure the deal for the diamond mining operation in South Africa.
\end{itemz}

\begin{itemz}[Notes]
  \item People think you are a respectable businessman, not an opium dealer.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cThief{}} The beautiful young woman you are courting.  There's just something about her{\ldots}
  \contact{\cCaptain{}} \cThief{}'s father, the captain of the {\it HMS Dauntless}; an intimidating man whom you're trying your hardest to impress.
  \contact{\cBoddy{}} He's the guy who's paying you to stick your neck out on the biggest opium run you've ever done.  He's also the guy who got all the opium onboard, and is supposed to tell you where it is.
  \contact{\cRobot{}} He's the little boy who works on this airship.  He reminds you of yourself at that age a bit. You've been mentoring him a bit, the poor child seems somewhat lost.
  \contact{\cNPCWhore{}} A lady friend you brought with you today for company.
  \contact{\cSaboteur{}} The author of one of the more recent books you've read.  He has some interesting ideas.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
  \memfold{If you see Badge \cCowboy{\MYnumber}}{Dear God, it's that bloody crazy American who tried to kill you that night!  What in God's name is {\em he} doing here?!}
  \memfold{Open at the start of game}{You fall to your knees as explosions rock the ship! What the hell kind of voyage is this?}
  \memfold{Open ten minutes into game}{Your pocket watch! It's been stolen! It was a very fine piece of jewelry, and it never leaves your side. Maybe you should go talk to the captain about this.}
\endtag

\end{document}
