\documentclass[char]{airship}
\begin{document}

\name{\cJack{}}

\bigquote{``Whores!''}{}

You are a warrior for God the Almighty. Though the world turns to shit
around you, you fight for goodness and decency. You follow the
strictest rules of behavior and work to enforce them in all people,
especially with your own family. Morality begins at home.

God has, of course, been testing you. But you are a devoted servant,
you stand tall under the weight of your misfortune, no Job-like
wailings escape your lips. Your trials come to you in the form of your
wicked, sinful family. You love them, of course, as God commands you
to. You are strict because you love them, because their souls need
saving. Your grieve for your failures, for your children who shall not
join you in heaven. 

Your dirty, sinful, horrible children. Dirty, dirty, so dirty! Out to
get you, to test you, to destroy all that is good! It makes you {\em
so angry}! You want to lash out, destroy destroy destroy.

Your eldest son, Augustine, was full of wickedness. He wanted so to
repent, and how long you prayed with him! You beat him, you took him
to church every day, you employed the most modern devices for
restricting the lust of men. But his wickedness was too great, and he
always reverted to his sinful ways. Not paying the utmost attention in
church. Looking at the lower limbs of ladies with lust in his
eyes. Having sinful thoughts. Not honoring you and his father
properly. Wanting more than the good Lord has provided to
him. Breaking the sabbath. Knowing he was so far from God, so drenched
in sin, drove him to madness, and he committed the worst sin, that of
self-slaughter. The boy is in the fiery pits of Hell for all eternity,
and you declared that his name would never again be spoken in your
home. You would not allow his wickedness to call out from Hell to
corrupt the rest of your family.

No, it was your mission to keep them holy and good or die trying. You
swore nothing would stop you, not your husband, not your dead son, not
the sinner and the whores...

Then there was your second son, Thomas Aquinas. Nasty boy, he brought
desecration to his holy name. You always called him by whole, proper
name, but he insisted on referring to himself by that vulgar epithet,
''Tom'' with his rascal friends. At least his brother tried to repent
his wicked ways. But Thomas Aquinas has no guilt in his soul. You sent
him to the strictest reform schools you could find, you prayed for his
soul night and day, you had others pray for him, you locked him in an
empty room with only a Bible to read and only visits from yourself and
the Vicar.

His father... oh, it makes your blood boil just thinking about
it... your husband was lenient. ''Boys will be boys!'' he said. ``He
will grow out of it, he is young!'' he said. Such a fool you
married. But what once was twain, now is one flesh.  ''What therefore
God hath joined together, let not man put asunder.'' You will be
together until the good Lord takes one of you from this Earth, even if
you both despise it.

Thomas Aquinas disappeared when he was sixteen. You never heard from
him again. 

After that it was just you, your husband, and your youngest child,
your only daughter. You swore not to make the same mistakes you made
with your sons. No one understood you. No one at all, they are all so
dirty, so corrupt, so sinful, disgusting, pathetic terrible dirty
whores and sinners, whores and sinners all of them... No, you told
yourself, it would not be the same with you and Abigail. Your husband
had turned melancholy after the loss of his wicked sons, drinking an
unconscionable amount of foul liquor and locking himself away in his
study. It was clear he grew to hate you. While you stay with your
husband because you made an unbreakable covenant before the Almighty,
you know he stays with you only for appearances and your wealth. While
he is of an old, noble name, his family has been most impoverished in
recent generations due to the sinful and wasteful behaviors of his
forefathers. He had wasted most of the money you brought to your
marriage. You have one surviving sibling, your elder brother,
William. William is very strange, but he adores you. He has never
taken a wife and leads a very simple, reclusive life. He has no use of
the wealth your parents left to him, and he sends you a very generous
stipend. If your husband were to try and divorce you, he would not
have access to your brother's money. It is of course horrible that
divorce is allowed at all in England, but even if he were to try and
divorce you, he would need to prove that you were adulterous, which is
beyond absurd.

Your husband was no help to you with Abigail. As he fell to sin, deaf
to your protestations, your anger, your prayers, so she fell. What did
you do wrong? She was the only child you had left, and you doted on
her. No girl could have asked for more love from her mother.

Abigail was interested in the most inappropriate things. She had no
conception of the proper place of a lady! A lady is saint. Her body is
a temple to God the Almighty, to be kept pure and clean. A lady
restricts herself to ladylike pursuits.

Abigail, though... she wanted to... to... ``tinker''. To take things
apart, and put them together. She wanted to study math and science and
engineering. Such madness! What was wrong with her? What demon could
possess her have such unnatural desires! How could she do such a thing
to you, who tried so hard to put her right!

Then one day, she disappeared like her foul brother before her, except
she left behind a note. A note that stabbed you in the heart, a poor,
broken mother's heart. 

\begin{quote}
Dear Mother,

Goodbye. I am leaving to escape your madness. Don't worry about me, I
can support myself. Don't blame Father, it is your fault I've been
driven to this.

Abby
\end{quote}

{\em ``I can support myself.''} Your own daughter, a whore. You stood
there, holding her note in complete shock for... you have no idea how
long. You never imagined it could be {\em this} bad.

You lost all hope there. If even your nearest and dearest, your own
flesh and blood, could fall to such darkness, then mankind is more
corrupt than you could have fathomed before.

For a long time you shut yourself away. You spoke to no one, directing
your servants through signs. You ate your evening meal with your
despicable husband. Your silence was broken only to recite the word of
God in the holy confines of the church.

Then something happened, almost a year ago, that made you realize how
selfish you had been being. Your husband had fallen to the most wicked
of ways: drinking, gambling, foul language, staying out late into the
night. One night he didn't come home at all. When he came in the next
morning, he clothes were askew, he refused to explain where he had
been and he had a ridiculous grin plastered on his face.

Of course. How could it be any other way? God was punishing you. You
knew what you had to do, and you had shirked your duty, and this was
your punishment.

Your own husband, with whom you are of one flesh with, one soul with
by the grace of God... turned to {\em whoring}. Whoring, the downfall
of Man, of England, of God's creation. They all go to the whore, the
men do. Leave their good, faithful wives praying and crying at home,
and go to the dens of whores, bringing back their vile influence and
sinful ways and the plagues God has sent down to destroy them in their
sin. But there are so few of those good wives left! So few, for the
women all turn to whoring. Young, old, pretty, ugly, they sell their
bodies to men, those breeders of sin! There is nothing more repugnant
on the face of the Earth than whores! Dirty Dirty Dirty Dirty Dirty
Whores everywhere everywhere! Surrounded by whore drowning in whores.

You could stand your life no longer. Everything around you had turned
to shit. Of course. How could it be any other way? God was punishing
you. You knew what you had to do, and you had shirked your duty. You
had been so selfish, only caring for yourself and your family! The
world needs you. Only you see the truth, the whole truth. You must
cleanse and purify, it is the will of God. You will start with the
source of sin, destruction, and filth, the despicable whores of
London.

It felt wonderful, to finally give yourself to the will of God. He had
been calling to you for so long, but you had made yourself deaf to
him! What a sinful creature you were! He made the corruption of the
world manifest in your own home so that You would not stand for it,
could not stand for it. You would take a stand, for all that is good,
and right. You'd purge the world of those foul creatures, one at a
time. They are easy enough to find, and if you squeeze their dirty
little necks hard enough no one can hear their lovely screams as you
send their souls to their well deserved judgment.

You are so happy to be doing the will of God. You must seek out other
ways to purify the world and serve your Lord. You know you are doing
the will of God, but you don't always remember exactly when or
where. You would find yourself walking home, with souvenirs from
girls, and then you would read about another death the next day.

They call you Jack now, they do. The Ripper. Ha ha, rip them up you do!
Oh, you would chop them all into little bits if you had the time, but
you never have the time, no, the sun is always coming and you must to
home, and clean off their dirty whore blood, get their impurities off
of you.

You plan to continue your crusade aboard this, the maiden voyage of the {\em HMS
Dauntless}. Your husband requires that you wear some trinket he dragged on board
to upkeep the fable of your marriage. It's in a locked box in your room, and you
think the captain of the vessel has the other key required to open it. Wear it you will - 
if it will get you closer to eliminating what it is you despise -

{\em Whores}!

\begin{itemz}[Goals]
  \item Serve God in any way you can.
  \item Save the world from sin.
  \item Destroy any whores you find.
  \item Keep all around you from coming under the influence of whores.
  \item Prevent men from consorting with whores.
  \item Maintain the fiction that you and your husband have a happy marriage.
  \item Wear the Neptune's Tear at the in-flight ceremony.
  \item Enforce strict standards of behavior in all those around you.
\end{itemz}

\begin{itemz}[Notes]
  \item You are unhinged and insane, but act normally unless provoked.
  \item It is up to you to decide how easily you are provoked.
  \item Your memory is filled with empty gaps.
  \item You are moderately dissociative - your sense of self and identity is often awry.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cNoble{}} Your despicable husband.
  \contact{\cCaptain{}} The captain of this ship.
  \contact{\cThief{}} The captain's daughter. Young, pretty thing, seducing the men with her feminine wiles. If she is not already a whore, she probably will be soon.
  \contact{\cWhore{}} \cThief{}'s tutor. You think you may have seen her out on the streets with the whores, but you are not sure. You don't like the way your husband looks at her. You know what to do with whores{\ldots} 
  \contact{\cVicar{}} The good Vicar who tried to hard to help you with your sinful children. He is a great comfort to you in your times of trial, and you are thankful he has returned from America, that sinful, whore-filled place.
%%  \contact{\cSaboteur{}} French woman. You know what they say about french women\ldots Probably another whore.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
%%  \mTest{}
  \memfold{Open at game start.}{A series of explosions rock the ship, throwing you to your knees. What can the matter be now?}
  \memfold{Open if you see badge \#230}{Oh! It's Abigail! \ldots{} Is she a whore, too?}
  \memfold{Open if you see badge \#236}{As you see the body before you, your mind recalls images of rose petals falling on the pure, English snow. Next time you are alone, open your $\alpha$ packet.}
  \memfold{$\alpha$} {You begin to reflect on
  the death of \cNPCWhore{\fullplain}.  It was good work on the part
  of whomever did it, but it quite the pity that you didn't get to
  destroy her yourself.  You know that you meant to get around to it.
  Hopefully, before take off even.  But somehow you got delayed.  Wait
  a minute?  What were you doing before take off.  You can't really
  seem to remember.  Sometimes, this has been happening of late.
  These gaps in your mind.  Once you even read about, what was clearly
  your handiwork in the Times one morning, but you couldn't seem to
  recall what you'd done the night before.  Not that it matters
  really.  As long as they get cleansed, you don't need to remember
  it.  Perhaps this is even the Almighty rewarding you.  You purge the
  world of sin and He purges your mind in return.  No matter.  You
  must keep up the fight no matter what, and now that you're done with
  \cNPCWhore{\informal} you can move on to...Wait a minute?  Maybe you
  didn't miss your chance to destroy \cNPCWhore{\informal}...}

  \memfold{Open two hours into game.}{Something threw you for a loop a few hours ago when you were talking with your husband, and you've been unable to place your finger on it ever since. Oh, you think you understand! His hands{\ldots} they looked ringless and bare. But it was probably a trick of the light.}



\endtag

\end{document}
