\documentclass[char]{airship}
\begin{document}

\name{\cRobot{}}

\bigquote{``Life is pleasant. Death is peaceful. It's the transition that's troublesome.''}{-- Isaac Asimov}

You remember everything that has happened to you. Your first memory is
of darkness. You didn't know what it was then. You heard the sound of
steam escaping, though you didn't know what that was either, a smell
you would later realize was a combination of the smells of
warm metal and human illness.

The first thing you did, upon taking in this data, was to open what
are known as eyelids. You were greeted with so much data! It was ever
so much more interesting than darkness. You saw two faces: your mother
and father. At the time, they were no more interesting than all the
other new things you saw. They named you William and mother leaked
water from her eyes.

Mother was always wonderful to you. She taught you so very many
things. Father stopped moving not long after you first woke up. Mother
told you he had died, and that that was how humans shut down
forever. She leaked lots of water from her eyes. She told you that was
crying. She said it was because she was sad.

You know what things happen around you, what humans do, but you never
understand why. You ask, and then they tell you, and sometimes you
understand, but when you think you understand something new, you are
often wrong.

One day you stopped being with Mother. You don't know why. It was nice
with Mother, and you did not want to stop being with her. Mother told
you she loved you and she had to put you away for awhile to keep you
safe. She kissed you and turned you off. When you were turned on again
strange people were looking at you. They gasped and one of them
shrieked, someone yelled ``It's ali-'' and you were turned you off
again. Next time you woke up your limbs were being restrained. You sat
up, accidentally breaking the restraints. You heard gasps again, and
something large grabbed you from behind and everything went dark yet
again. It was all very confusing.

Things like that kept happening to you until finally a man told you
that he had bought you. He told you his name was \cBoddy{\intro} and
that you were going to work on an airship. Your mother used to make
airships before she made you. She was very, very good at it. 

He took you to his ship, which is run by \cCaptain{\intro}. He is nice
but you think he seems sad. It is hard to tell what people feel. 

Now you spend most of your time now with \cCid{\intro}. She teaches
you many things. Everyone else thinks she is a boy, and she told you
can not tell anyone that she is actually a girl. You really do not
understand, but she says it is important. When \cCid{} is not teaching
you things, you shovel coal and do whatever the crew tells you to do.

There are other people around the ship. You are trying so hard to
understand them! \cNPCWhore{\intro} is very nice to you. She is here
with a man, \cDealer{\intro}. He is also your friend and tells you
about the world! You like having so many friends. \cNPCWhore{} gave
you a very pretty ring to play with. You keep it with you all the time
and play with it. You even wrote her a nice letter and put it in her
room.

\cThief{\intro} is the Captain's daughter and she is also nice. She
comes down to see \cCid{} a lot. You hope she likes you. Her uncle is
\cVicar{\uncle}. He's a vicar and he talks to you about religion and
God. You really don't understand that. It is even more confusing than
people, but he really likes to talk to you about it, so you stand and
listen. You are good at this.

You feel like you are different from the other people somehow. You
want to be like them. You bought a book several hundred hours ago, and
you will read it soon. It is called ``Miss Manners' Guide to Raising a
Well-Mannered Young Gentleman''. Maybe if you read it, you can be a
well-mannered young gentleman. You are not entirely clear what a
well-mannered young gentleman is, but it sounds like a good
thing. Maybe some of your friends can help you learn what it is. They
all have so many different ideas, though, and you don't know who is
right. You'll have to listen to them carefully.


\begin{itemz}[Goals]
  \item Be nice.
  \item Help Cid keep the ship running.
  \item Read the book and become a well-mannered young gentleman.
\end{itemz}

\begin{itemz}[Notes]
  \item You are a clockwork metallic automaton who looks like a real boy. You do not bleed, although you look identical to a small blond boy.  Everyone around you expects you to be what you look like, and generally have no clue about your true nature.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cRobot{}} This is you. You have met you. You try to be nice and fix things.
  \contact{\cCid{}} A nice girl. She tells you to do things.
  \contact{\cCaptain{}} A nice man. He captains the ship you work on.
  \contact{\cBoddy{}} A nice man.
  \contact{\cDealer{}} A nice man.
  \contact{\cNPCWhore{}} A nice lady.
  \contact{\cVicar{}} A nice priest man.
  \contact{\cThief{}} A nice girl. She comes to see Sid.
  \contact{\cCowboy{}} A nice man.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
  \memfold{Open at the start of game.}{A series of explosions rock the ship, and you are thrown to your knees. Uh-oh.}
  \memfold{Open if you see badge \#532}{It's mother.}
% bryce
\endtag

\starttag{abils}
  \ability{Robotic Body}{Your CR is 1, except for the purposes of being {\bf Wounded}. Then your CR counts as 4. You may also ignore one bullet per hour. If you are ever {\bf Wounded}, you fall unconscious and can recover fully in five minutes. When your character falls down, make a ``clunk'' sound. If anybody examines your {\bf Wounded} body or attempts to perform {\bf First Aid} on you, tell them that your innards seem to be entirely mechanical. Note that you can still be hit with a {\bf Killing Blow}.}{...}
\endtag

\end{document}
