\documentclass[char]{airship}
\begin{document}

\name{\cThief{}}

\bigquote{``The restlessness that comes upon girls on summer evenings results in lasting trouble unless it is speedily controlled. The right kind of man does not look for a wife on the streets, and the right kind of girl waits till the man comes to her home for her. ''}{-- Sedalia Times}

Daddy always said that young ladies are best when they are seen and
not heard. When they are quiet, polite, reserved, and utterly
unambitious. ``{\it No man will want to marry a female version of
himself}'', he's fond of saying. ``{\it A man wants to marry a {\bf
lady}: one who conducts herself at all times with the utmost of grace,
charm, decorum, and civility.}'' You've certainly tried to be your
father's daughter. Every morning you awake to a long day of the three
pinnacles of young womanhood: music, history and etiquette lessons to
be learned from some fastidious and stern tutor. You enjoy the first
of these much more than the last two. You've always had this wonderful
voice, one capable of stunning crowds of listeners and bringing tears
of joy to your instructors. You have amazing range, strength, control
and stage presence, and it is something of which you are very
proud. So you sing for two hours every morning, and the songbirds
outside chirp happily with you, before going on to endure the rest of
the day's lessons. Your voice hath charms to tame the savagest beast,
Daddy likes to say, pretending to be pompous. He is a serious man,
though, and insists on you knowing your European history as well as
the historians of the thick dusty books he has you read. He fought in
the Steam War, he constantly reminds you, and understands the value of
not letting history repeat itself. Sometimes you worry for him. Daddy
has so much on his shoulders nowadays ever since he decided to oversee
the construction and maiden voyage of the {\it HMS Dauntless}. He
forgets that his doctor told him to try to live a calm life. He
suffers from some internal condition ever since a terrible accident
during the War that pierced his body with little bits of metal. You've
asked him about it, but he says the story is not becoming for a young
lady to hear, and you don't press the issue.

But you know how much this voyage means to Daddy, even if he doesn't
want to admit it. He thinks of this as his greatest project ever, and
to be honest, he is so involved with it, he has even started paying
less attention to you. This newest tutor that he hired, Miss Watson,
she's decent, but it's nothing compared to the stellar instruction you
have received previously. She is a fine lady, and reasonably
intelligent, but it always seems like her mind is elsewhere. The
problem is, you're not sure what she what she is constantly thinking
about all the time, if her job is to tutor you. Even her singing is a
little strange. She sometimes seems like she's not entirely sure what
she's doing, but father hired her, so you obediently train under
her. A strange lady.  One of her actions caught your eye, recently. As
she passed by you in the hallway, you could swear that as her skirt
moved along the ground, you saw a small stilleto tied to her ankle.
You're sure father would not approve, and you've been meaning to ask
her about it.  Despite this oddity, Miss Watson is just as easy to
fool as the others about your nighttime activities. See, very few
people know that there is a whole other side to you. While the rest of
the house is asleep, you sneak out by climbing down the tree branch
outside your window, and go out exploring the night. You can't quite
explain it, but since an early age you've had this most strong desire
to {\it take things}. Not necessarily valuable or expensive things,
but things you are not supposed to have. You take other people's
things, while they aren't paying attention. It's so much easier than
you could have imagined, and so fun and liberating. You've taught
yourself to be a pretty decent pickpocket and lockpick at this point,
with no small amount of heists under your belt. You're not sure what
Daddy or Miss Watson would say if they found out that you are a thief
come night fall, but you are determined not to let them find out.

It's been harder and harder to go out at night, because your uncle,
the Vicar, has been staying with you. For some reason he has decided
that your virtue is his to preserve. You love your uncle. He has
helped take care of you ever since you were a small girl, ever since
your mother died. His silly antics, like falling asleep outside your
door, and requesting a bedroom next to yours, just make you giggle and
blush. But then again, he has been looking a little out of sorts
lately. Ever since he came back from America, there have been dark
shadows under his eyes, which seem to melt away every time he hears
you singing. Uncle looks very grave when he talks to you, and goes on
at length about how vile and mean the world outside Daddy's protective
environment can be. Little does he realize how much you know about
such a world! Well, not about the aspects that have to do with men, of
course! You turn scarlet red at the thought. You may be a thief, but
you're still a {\it lady}, you tell yourself. But Uncle looks paler
and more world-weary than usual since he got back from traveling
abroad, so you try to be nice to him.

Well, you have met someone. But you're not sure Daddy would
approve. His name is Evan Bryce, and he's a businessman of no small
import who's been making subtle gestures that he's contemplating
asking your hand in marriage. The fact that he is a {\it nouveua
riche}, and not some refined class of noble, might offend Daddy's
sensibilities, but you don't much care. He's nice and polite and
charming, but almost too much so. You sense something in him,
something he is trying to hide, whether he knows it or not. Something
exciting and wild like you, but all of your attempts to bring it out
have been in vain. You sigh. A very nice man, but certainly not worth
marrying. If only he could crack safes or break into banks, then you
would swoon in an instant. Instead, you think nothing of the kind
could ever come from him. He's too clean, too proper, too bent on
impressing your father. Oh, well. He's still got time to lighten
up. You're not done trying, and you will never marry a stuffy noble if
you can help it. Luckily, he'll be along with you on the voyage, and
you can have some fun with him there. You like him so much, you even stole his pocket watch while he wasn't looking! Maybe you can taunt him with it at some point. If father ever found out, he'd toss you off the ship{\ldots}

Oh, speaking of the voyage! Do you ever have plans for the voyage!
First of all, Daddy wants you to perform in a short solo concert for
the guests during the Dedication of the maiden voyage. This should
be easy, but you've been feeling a little sore in the throat lately,
and your pitch is not entirely on. You definitely will need to get
Miss Watson or somebody else to rehearse with you at least several
times before the performance. Second, and this is has kept you awake
giggling at night, several nobles will be on board. One of their
wives, Lady Gwendolyn Major, is scheduled to display her world famous
necklace, ``Neptune's Tear'', shortly before your performance. As soon
as you saw it in the newspaper, you realized that you had to have
it. Absolutely had to. And this is your chance. You know that Lady
Major has to remove it at least at once tonight to show to people, and
you should plan around that time - and steal it either before or after
its presentation.

If Daddy ever caught wind of this, he would probably be very upset,
and frown and mumble something about there being too much of your
mother in you, then say some words a young lady should never repeat as
long as she lives, even in the company of drunk sailors (not that a
young lady should ever be in the company of drunk sailors, Uncle
warns!). You wonder about her - your mother. What was she like, before
she passed away? In private, Uncle has told you that your voice is as
beautiful as hers was, that you sing just like her, and that there are
other qualities of her in you. You have to admit you're terribly
curious, but what girl wouldn't be? 

You have some memories of your mother... You remember standing at a
parade with her, holding her hand and gazing up at her... she was so
beautiful and strong in your eyes, and you thought she could do
anything... but she couldn't live to see you grow up. You know it
wasn't her fault, but sometimes you almost blame her for leaving
you. It's been hard growing up with your only older female role models
being distant and stuffy tutors. If only your mother were still
alive. Some of your memories of her are confusing... people shouting
and fighting, and you sobbing... maybe your parents were fighting?
Were people talking in French?  You've never been able to ask your
father, of course. You can't imagine what she could have done to hurt
father so. You can see instantly why she married him, though. The old
faded photographs show quite a cutting image of a wartime hero,
scruffy, rude and aggressive, with the world before him and laughter
all around. You want a man like that. Better yet, you sometimes want
to {\it be} like that. But nobody would ever approve such a thing, and
you're ashamed for thinking it. Maybe this is why you like Sidney, one
of the engineers who flies the {\it Dauntless}, so much. He's always
cursing and drinking and covered with oil and grime and having a good
time. You gave him a kiss once in the boiler room, and he was so
shocked that he jumped three feet in the air, hit his head on a pipe,
and rolled down a flight of stairs. So from now on you always try to
give him a hard time and flirt with him. Just as long as father isn't
watching{\ldots}


\begin{itemz}[Goals]
  \item Train up for your singing performance at the Commemoration.
  \item Steal the Neptune's Tear!
\end{itemz}

\begin{itemz}[Notes]
  \item Despite your larcenous activities, everybody still thinks you're a Daddy's girl. You're sort of trying to keep up the appearance.
  \item There's little you wouldn't do to see Evan loosen up a bit{\ldots}
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cCaptain{}} Beloved Daddy. You fear for his health almost as much as he fears for your upraising.
  \contact{\cCid{}} A cute engineer who works down in the mechanical section of the ship. He's certainly much more exciting than Evan...
  \contact{\cWhore{}} Your unimpressive music, history and etiquette tutor.
  \contact{\cDealer{}} Marriage material. If only he weren't so boring and proper.
  \contact{\cBoddy{}} One of Daddy's wartime friends who accompanies Daddy almost everywhere.
  \contact{\cVicar{}} Your Uncle, and a stern righteous man.
  \contact{\cCowboy{}} A strange man your Uncle brought back from America
  \contact{\cRobot{}} The adorable little boy who works on your father's ship. He's always with \cCid{}. Not only is \cCid{} cute, he's also good with children!
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
  \memfold{Open at game start.}{A series of explosions rock the airship! You are thrown to your knees, heart racing. Oh, you hope Daddy is okay!}
  \memfold{If you see {\bf item \# 35-C} or {\bf item \# 152}.}{{\em Oh, darn it! Daddy told you the combination to this lock once, but now you've gone and forgotten it!} Stand within ZoC of the item for one minute and look pensive. You may then open your {\bf L Packet}.}
  \memfold{If you see {\bf item \# 35-B}.}{{\em This lock looks like it fits Daddy's big key. You palmed a second copy of the key a few nights ago while touring the airship. The last place you remember having it, though, was in one of the engineering rooms in the back, when you kissed Sidney{\ldots}}}
  \memfold{{\bf DS Packet}}{This must be where the key fell out of your pocket when you were in here with Sydney. If you spend one minute examining the sign that prompted you to open this packet, you may retrieve the item that is taped to the back of it.}
\endtag

\end{document}

% LocalWords:  upraising Daddy's abils
