\documentclass[char]{airship}
\begin{document}

\name{\cVicar{}}

\cenquote{``He that is slow to anger is better than the mighty, and he that ruleth his spirit than he that taketh a city.''}{Proverbs 16:32}

You have always thought that the Lord sends a person no more suffering
or temptation than He knows they can withstand. He does not punish,
He tests. In light of the trial you find yourself in, either He has a
much higher opinion of you than you do of yourself, or your prized
axiom is incorrect, and you have transgressed gravely from the path of
the righteous.

You have recently returned to England, your beloved homeland, and are
currently staying with your brother, \cCaptain{\intro}, and your
niece, \cThief{\intro}. The Archer family is a small one, but
close-knit by bonds of love. It would have been larger, perhaps, had
the bond between John and his former wife \cCurie{}, been as
strong. She was quite a match for your brother, with a vibrant
personality, a brilliant mind, and a voice to bring men to tears, in
song or in rage. Sadly, the war and the birth of little Mary Elizabeth
engendered enough differences between them that they sought
divorce. John was granted custody of Mary Elizabeth, but his former
wife wanted the child for herself and ran off with her. They were
found a few months later after great effort on the part of your
brother and his good friend, \cBoddy{\intro}. \cCurie{} was sent to
prison and banned from contacting the child, which was perhaps a bit
overharsh. You've heard nothing of his wife since. Your brother
prefers that way, and although you have urged him to thank God for
both the happy times in his marriage and the lessons learned from
duress, he has never mentioned \cCurie{} since then without spite. In
fact, he's gone so far as to tell his daughter that \cCurie{} is dead.

Your sleep is plagued with horrifying dreams - your family or friends,
gutted and shredded, victims of a madman. The nightmares, only
troublesome at first, accquired such a persistence and regularity that
your temper began to strain. You've always tried to walk the path of a
good man, kind, caring, a steady one for others to rest against in
their times of need. But now, where you tried to find the good that
God has placed in every person and situation, you see little besides
sin, or corruption creeping towards innocence.

Mary Elizabeth is a splendid young woman now, nearing marrying
age. John has raised her well, and protected her from harm and worry
without fail - which is, oddly, a cause of concern for you. Mary
Elizabeth is of the age when certain, ah... {\em concerns} arise, and
with John being preoccupied with both the launching of {\it The
Dauntless} and finding a suitable husband for his daughter, you have
taken it upon yourself to make sure Mary Elizabeth stays free from any
undue influences, any{\ldots} inappropriate contact. Perhaps you are
doting, a little, but you have no children of your own, and are every
bit as protective of her as her father.

In fact, you've been nearby for all her life; when John departs on
hazardous tours of duty, you're the one who cares for her, so
perhaps it is not so foolish to feel more like a second father than
merely an uncle. The longest you've been away from Elizabeth was
during your recent trip to America.

Several of your friends from seminary now live there, and one of them
invited you to visit for a time. You jumped at the prospect, and
planned a lengthy trip to visit several of your old friends and assist
them with their frontier churches. It was invigorating, discussing
theology with old friends and new faces, but also exciting to see a
new part of the world, even one as rough and largely uncultured as the
American countries are. You were even one bitten by some sort of wild
animal, a coyote, it was called, for goodness sake!

One of the new faces you've met is \cCowboy{\intro}, who is quite
possibly a philisophical genius despite his humble station. He helped
you out of a nasty confrontation with some ruffians - he cuts quite an
imposing figure, with those clanking metal legs of his - and when his
philosophical aptitude came to light in your following conversation,
you invited him to come with you to meet the friend you were staying
with. You and \cCowboy{} became friends quite quickly, and he traveled
with you on the later part of your trip through America, serving as
guide, guard, and rhetorical sparring partner. Not only does he hold a
number of very radical views, but he's also a former Christian - he's
said a number of times that he was quite faithful when he was
younger. You've dedicated yourself to the cause of returning him to
the arms of the Lord.

Unfortunately, you are frustrated in this regard by his recent
fascination with the works of \cSaboteur{\intro}, chiefly his novel
''Ragnarok''. It advocates the most bizarre doctrine, exhorting the
common man to rise up against those of higher station, and then goes
so far as to suggest that this will create a wholesome, peaceful
country! It's as if someone had suggested that people could build
houses by dashing rocks and trees to pieces upon the ground! But
\cCowboy{} doesn't see any of that. He sees only the promise of a
brighter life for the downtrodden. His eyes light up with an inspired
fire when he argues in his defense - a fire you know should be kindled
instead by a holy faith in the Lord. Curse that damnable man and his
poisonous writings! To prey upon the misfortunate by offering them
false hope and appealing to their basest instincts! To cause a
straying son to tarry longer from the Flock! You're not prone to such
outbursts, but the injustice and raw deception{\ldots} it makes your
blood seethe.

You thought it was the strain at first, from those terrible dreams,
but you know now that this{\ldots} emotion cannot possibly be natural. It's
{\it always} there, sometimes a slight grating of annoyance at the
base of your skull, sometimes temple-pounding rage. Directed at
anyone. Everyone. Were it not for your faith in God, your unshakable
adherence to the ideals of the Savior, you would have certainly by now
taken a knife and sought to kill your brother, or - Heaven forfend -
Mary Elizabeth, to rend their corpses until they matched their state
in your dreams. And, you fear, the faith that has steered you through
your life, through trial after trial, may be slipping.

A few weeks ago, you recived a telegram from John, saying that his
grand project, {\it The Dauntless} had finally been completed and the
British government was sponsoring its maiden flight to Paris on New
Year's Eve. You cut your trip short, knowing how much this event meant
to your brother, and invited \cCowboy{} to come with you, since he had
mentioned a desire to see England. You hope he takes well to your
homeland.

You are overjoyed to be reunited with John and Mary Elizabeth. It
would seem she has aquired suitors since you left. While you wish for
her to know the joys of matrimony and family, it is imperative that
she wed only the best. Marriage is forever, and you would not have
your darling niece forever chained to a man you have not thoroughly
vetted. One of her suitors, \cDealer{\intro}, you have not yet met,
though you are told he will be on tonight's voyage. John has expressed
his concern that one of the ship's crew, a young man named
\cCid{\intro}, may be persuing Mary Elizabeth. You do not think his
station is equal to hers, but you are willing to give him a chance to
prove himself. There is no need for Mary Elizabeth to rush into
marriage, and if neither of these men are an appropriate mate, well,
there are plenty more.

Another item of minor annoyance has come up. John has recently hired a
new music tutor for Mary - \cWhore{\intro}, whom you've taken a
passive interest in. Not only does she seem to be a lower quality
instructor than some of the previous stars John has hired, but
something is different about this one. You're not sure what it is that
you sense, but you don't like it. She seems {\ldots} like a dirty
girl. Like she could blend into the dirt of the streets if not for her
dress and manners and station. You've been trying to be careful about
judging, lest ye be judged yourself, but your feeling about this one
is unmistakable. She's hiding something. But John has entrusted the
raising of his daughter into the hands of this young woman, and that
is good enough for you, you think.

Sidney's assitant, \cRobot{\intro{}}, is a delightful young child, and
suprisingly intelligent for a coal-shoveler. Sidney has been aiming to
train the lad as an engineer, despite his youth, but you can see even
greater potential in him. You're determined to encourage him to take
an interest in religion - if he did, you're sure he'd become a pastor
of great renown. But you're no longer certain that \emph{you} are fit
to teach him. Not with this darkness plaguing your thoughts.

Why, God? Why has He seen fit to visit this curse upon you? What
\\presence dwells inside you that images and impulses of slaughter visit
you without end?

What purpose could such a trial serve?

\begin{itemz}[Goals]
  \item Return \cCowboy{} to the true path.
  \item Tend to the religious wellbeing of the passengers of the {\em Dauntless} as needed.
  \item Keep ahold of yourself...
  \item Encourage \cRobot{} to explore his faith.
  \item Help your friend \cJack{\intro} through her difficult times.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cCaptain{}} Your brother, captain of the ship. A fine man.
  \contact{\cThief{}} Your niece, a proper young woman, whom you feel responsible for. She has just turned eighteen.
  \contact{\cCowboy{}} A recent traveling companion and friend. You want to reconvert him to Christianity. It seems that he recently damaged his mechanical legs.
  \contact{\cWhore{}} Mary's music tutor. You don't have a terribly high opinion of her.
  \contact{\cRobot{}} A young boy who works with the ship's engineer. You couldn't bear the thought of any harm coming to a child like him.
  \contact{\cCid{}} The ship's engineer, a loud, brash young man.
  \contact{\cCurie{}} John's former wife. You're not sure how her prescence is going to play out.
  \contact{\cSaboteur{}} A horrific man who misuses his talent for writing to delude the misfortunate.
  \contact{\cJack{}} One of your parishoners, a very devout woman, but also very strict - she's had a hard time raising her children, and often came to you for help. Her eldest son was obsessed with his sinful nature, and tragically took his own life. Poor \cJack{} was never the same. Her two younger children are no longer living at her home and she refuses to say what happened to them. You wish you could help her more in her trials, though you know her faith in the Almighty will see her through.
  \contact{\cNoble{}} \cJack{}'s husband, a prominent politician. He does not seem to be as devout as his wife. Still, you wish to help their family in anyway you can. 
  \contact{\cDealer{}} A young man seeking Mary Elizabeth's hand in marriage. Only a true gentleman will do for dear Mary.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
%%  \mTest{}
  \memfold{Open at game start}{{\it Explosions rock the ship.} Goodness! You'd better check and see if anyone was hurt \ldots{}}
  
  \memenvelope{W Packet}{{\it You may expend 3 Grace to delay the effects of this packet to until you gain another Sin point. You may suffer the effects of this packet multiple times per game.} Put on the enclosed red headband and namebadge. Your CR is now 4. The only attack you can make is an unarmed wound attack, and you are immune to bullets unless the firer shouts ``Silver". Attack people, starting with anyone you are particularly angry at. You return to normal if: \begin{enum}
\item You reduce 2 people to unconciousness. Your Sin total is reduced by 4 in this case.
\item You are knocked unconcious or wounded.
\item You are instructed to by an ability card.
\end{enum}
 In any case, remove your headband and switch your nametag back. You are unconcious for 5 minutes after reverting. You do not accrue Sin while under the effects of this packet.}

  \memfold{Badge \# 539}{\ldots{} blood, blood. Everywhere, filling the air\ldots{}}
\endtag

\starttag{abils}
\ability{Preach}{You must have a positive {\bf Grace} stat. When you play this ability card, it affects anybody within your range of vision. Roleplay a preaching priest for thirty seconds, and decrease your {\bf Grace} by one.}{You feel bathed in the light of something divine. Increase your $\chi$ stat by one, or if you do not have a $\chi$ stat, tell me so.}
%%

\endtag


\end{document}
