
%%WHORE
%%--investigate Opium Dealer
%%--investigate Saboteurs and stop them
%%--investigate Boddy --> investigate his murder
%%--arrest Jack the Ripper
%%--train the thief to sing/be cultured
%%--sleeping with Noble for intel
%%
%%WHORE
%%--hired by CAPTAIN
%%--music / dance / theater teacher to THIEF
%%--wants to lure out JACK so she pretends to be a whore
%%--trying to catch SABOTEUR since she's a Scotland Yard
%%%%%

\documentclass[char]{airship}
\begin{document}

\name{\cWhore{}}

\bigquote{``A detective sees death in all the various forms at least five times a week.''}{-- Evan Hunter}

{\it A dark alley rises into prominence out of the streets of London before you. Hanging ladders, rotting refuse and the filth of human living cloud and attack the senses. You walk, briskly, holding your purse close, and careful not to trip over your long and full pleated dress. Steam, the ruler of the age, rises from a pothole in the ground, and shines a vivid yellow from the moon that stares at it from above, between buildings. You turn a corner - and find him, looking like you've always imagined him. Beady eyes set alongside tight and menacing cheekbones. A lithe body matted with dirty clothes and wild hair. An ugly nose protruding from a face too engorged in its actions to notice. On the ground before him is a mockery of humanity, a young woman that has been gutted and carved into pieces by the rusty, rusty knife of her attacker. Jack the Ripper turns to you slowly, blade raised and colored deep scarlet. He drops his prey and proceeds, evenstepped, towards you{\ldots}}

And with a rush of primal fear and a scream of terror, you wake from the nightmare. It seems like you've been having that dream more and more often now. The other agents at the Yard tell you that this is the price of your obsession with such a high-profile criminal. That this is why you're not allowed to investigate the case, and are usually given much more nuanced assignment. Let the gumshoes scour the streets of London, and have their epic battle with The Ripper when he finds them, they say. You disagree. Jack the Ripper is the nickname that the Scotland Yard and half of London have ascribed to a theoretical serial killer who has taken half a dozen lives in the last year. There's method in his madness, however, as all the victims seem to be loose prostitutes, and many of the murders are done late at night, in an ally or whorehouse or under a bridge. A knife is always used. The results are catastrophic. Multiple stab wounds all over the body with an emphasis on disfigurement and destruction. Half the victims the Yard examines just don't look human anymore. Of course, there's nothing to say that this has to be the same person, but your detective's intuition tells you so. 

The other agents downplay this series of slayings, and joke that maybe Jack will return some virtue to the city. The whores are asking for it by not quitting their base profession, they claim, but you feel a more idealistic calling. Human life is a precious thing, even if it is marred in sin, and Jack the Ripper deserves to be brought in. Some of the girls out in the dirty streets of the city are a day's pay away from starvation. The terror they must feel each night trounces your cautious reverential fear of the murderer. Ever since you saw his first victim's corpse, you vowed to get revenge. As one of the few female detectives with the Scotland Yard, you felt that this case was somehow yours from the beginning, yours before you knew it, and yours, certainly, no matter what the rest of the Yard has to say about it. So you've tried to catch him. As part of your infiltration of the streets of London, you apprenticed yourself to a lady of the night and learned how to strut, what to wear, the secret language of lecherous and drunk men. You pass splendidly for a whore, and you've often wandered the city streets at night, looking for trouble. This is a part you can play very well. A whore on the outside, avenging detective behind closed doors. It's served you well for the past few years, and even some of the other agents have begun to affectionately nickname you "The Whore". But Jack has not yet come for you, so you try harder, and feel like a fly walking into the web of a very unpleasant spider{\ldots}

But you should try and get that off your mind. You are here, about to board the {\it HMS Dauntless} for more important reasons. The {\it Dauntless} is a new breed of airship, and its fearless commander, Captain John Archer, is looking to dazzle all of Europe by taking the thing out for a test flight. Some pretty influential people will be on board, among them Lord Blackwell and Lord Major, two of the Empire's most powerful politicians. Like all statesmen, these boys aren't clean. You're sure at least one of them has had a hand in the opium craze that's swept the city and is in constant danger of undermining, or ever overthrowing, the law. Their purpose is unknown, but very shaky, confidential sources report that there is to be something of an opium deal tonight, with lots of money and lots of substance just dying to trade hands. You are to find out who is involved, what the proposed deal is, collect evidence to back you up in the notoriously unfair court trial that the politicians will receive, confiscate the cash and the goods, and arrest the conspirators. In short, you've been tasked with breaking whatever diabolical scheme is going on wide open. But that is not your only criminal-related business at the moment.

See, the {\it Dauntless} is a symbol of British pride. If it were to fail to make the journey, or never arrived at its destination, the reputation of Her Majesty's Engineering Corp would be in tatters, and the international economy would take a hit. Normally, such world-wide matters are not the concern of Scotland Yard, but there are British civilians on board, particularly said politicians, and they must be protected. So you are also to ensure the security and stability of the ship. There is no reliable intelligence as to what dark forces are working to ground the {\it Dauntless}, but they cannot be allowed to succeed. Find out if there are any saboteurs and terrorists among your ranks, and arrest them before they can damage the ship. But be forewarned: the Yard is currently combatting rumors of being very eager to arrest and interrogate anyone who so much as blinks an eye. If one of the politicians were wrongfully arrested, and the charges did not stand in court, the repercussions could be dire. Let's just say that Scotland Yard's budget could get very small in Parliament very quickly. Thus it is important that you gather evidence to support your beliefs.

This Lord Cornelius Blackwell person? Rotten to the bone. The money he must have shafted his Conservative Party to fund his own personal expenditures is beyond your estimation. A mole close to Blackwell reports that the pig has something planned tonight, some sort of opium deal. It's a well established fact that the backbone of Blackwell's operation is cutting deals between rightist groups and the London mob, but this is too much. An exchange of dark powder on an occasion such as this? Nothing is sacred anymore.

And so you walk a fine line with the nobility. They must be protected at all costs. If even one of them does not make it back from the flight, and the press found out that a Scotland Yard member was on board, the fallout would be very bad. If two or more voting members of Parliament came back in body bags, it could be catastrophic. Their lives are a high priority. Sure you suspect them of being corrupt and trafficking in opium. But that is something for which you will quietly arrest them, and with proof. Which brings you to your travel arrangements. Your cover aboard this flight is particularly ingenious. You needed some reason to be very close to the Captain, in case anything goes wrong. The Yard overstretched itself, but for a good cause, to get you to be hired as the Captain's young daughter's music teacher. A nice girl, Mary Archer, but you sense something a bit wild in her sometimes. The Captain of course expects your tutelage to be far more than simple music lessons with a bit of history about composers. You are also expected to raise he to be a proper young woman, polite and courteous and charming. That is the dual nature of such a position, and the way things are done. You're willing to devote yourself to this, until duty calls, that is. Because you're not supposed to drop your old cover. You're pretending to be a whore pretending to be a personal music tutor. If the Captain ever ``discovered'' your ``real identity'' as a lady of the night, he would no doubt be furious, but it's crucial. Whores get around in this society, whether one accepts it or not. Men tell you things, give you things, assume that you are stupid, say too much too easily. It's a wonderful information-gathering technique, and you are certain that some of the men aboard the {\it Dauntless} would like nothing more than to be seduced by a young woman such as yourself.

There is also the fact that, though you don't want to admit it to yourself, you hate not pretending to be a whore. Only for a few hours of the day are you not dressed and acting like a prostitute. Because if you are not a fly when you happen upon the spider's nest, he will not attack you. And then you will have passed up a chance at finally stopping Jack the Ripper{\ldots}

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Catch Jack the Ripper.
  \item Stop any attempt to sabotage the {\em Dauntless}.
  \item Stop Blackwell's opium deal, and bring him to justice.
\end{itemz}

\begin{itemz}[Notes]
  \item Your real name is Emily Knight, like it says on your Scotland Yard badge. ``Judy Watson'' is the cover name you were hired under.
  \item Be careful not to blow your cover unless absolutely necessary - you have a role to fulfill. Some people think you are Mary's tutor.
  \item The way to Jack is by pretending to be a whore. The more people who think you are a whore, the better your chance of drawing a confrontation. But be careful out there.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cCaptain{}} Your employer. Doesn't seem to suspect your true identity.
  \contact{\cThief{}} The young girl you barely have time to teach how to be a proper young woman.
  \contact{\cVicar{}} Her uncle.
  \contact{\cBoddy{}} A snake. Hopefully you can drag him home in chains when all this is over.
  \contact{\cNoble{}} A politician you have been having sex with to gather information.
  \contact{\cJack{}} His wife, whom you have not actually met
  \contact{\cCid{}} An attractive young man who works on the ship.
  \contact{\cRobot{}} A little boy who works with \cCid{}.
  \contact{\cSaboteur{}} A famous French writer.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}
  \memfold{Open at game start.}{A series of explosions rock the ship, and you fall to your knees. You didn't think the saboteurs would get started {\it this} early.}  
\endtag

\end{document}
