%%%%%
%%
%% Whitesheets live in this directory.  This file doubles as a
%% latex'able example whitesheet.
%%
%% Whitesheet macros (in ../Lists/white-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given whitesheet.  However, you can also
%% just use \name{Some Text} if you want.
%%
%% Note that for whitesheets, \name doesn't actualy typeset anything.
%% If you want the ``title'' of the IG document to appear, typeset it
%% how you want it.  Similarly, no ownership information appears on
%% the sheet.
%%
%%%%%

\documentclass[white]{airship}
\begin{document}

\name{\wOpiumPlot{}} %% used as a label, doesn't typeset anything

{\it This desk is completely covered with letters, books and scrawled notes on crumpled pieces of paper. The notes are represented below. They look as is they are for an upcoming speech. This item may not be moved or destroyed - it is a huge pile of paper.}

{\bf
{\ldots}compliment rest of dedication {\ldots} sure Mary will sing wonderfully{\ldots} Reginald can surely put something together.
\\
{\ldots}
\\
talk about history with John{\ldots}Steam War and victory{\ldots}how much ship means to him{\ldots}esteemed fellow travellers{\ldots}
\\
{\ldots}
\\
two individuals looking for something{\ldots} know who you are{\ldots} sure it will be an interesting flight
\\
{\ldots}
\\
all the regular blessings and endings{\ldots}deliver charge
\\
{\ldots}
\\
}

{\it Some diagrams follow. They show a crude sketch of the airship. Some points are noted with scrawled notes. A triangle overlays the entire ship, its center marked with a large X. If you have an {\bf PI Packet}, you may open it in approximately one minute. Do not open it in sight of other players.}
\\

{\it One of the worn, yellowed pieces of paper is adorned with crude doodles: France on fire, a raging English lion with four arms, and black scribbles coming out of the eyes of a poorly drawn skull.}

\end{document}
