
\documentclass[white]{airship}
\begin{document}

\name{\wHistory{}} %% used as a label, doesn't typeset anything
History of the World, Part I

Timeline of Events:

*1760-1830: First Industrial Revolution
\TODO{58 years pregame}

1845: Texas (for God only knows what reason) does NOT join the Union.
Further attempts to join the Union after this date fail, especially
after Texans manage to gain some knowledge and skill at keeping
European nations (that held NA lands) at bay.  Instead, it is it's own
nation. \TODO{43 years}

1846: The United States offers Charles Babbage a grant in order to
build his analytical engine, after the British government refused to
do so 4 years prior.  Babbage accepts the grant, fine-tunes the
design, and begins construction within a year.  In his spare time, he
also develops the plans for a second differential engine, which the US
government also funds to be built in 1849. \TODO{42 years}

*1848: Charles Louis Napoléon Bonaparte wins the French presidential
 election \TODO{40 years}

*1850: Start of Second Industrial Revolution \TODO{38 years}

*1851: President Bonaparte overthrows the Second Republic; declares
 himself Emperor Napoleon III, establishing Second French Empire \TODO{37 years}


January 14, 1858: Felice Orsini and his accomplices assassinate
Napoleon III in Paris with explosives made and tested in England.  It
also involved French émigrés living in Britain.  Absolutely huge
anti-British sentiment in France; politicians capitalise on this
sentiment to gain power. \TODO{30 years}

February 13, 1858: France declares war on Britain.  The Steam War begin.

The Steam War is so named because of the fact that it took place
during the Second Industrial Revolution.  The British and French
warmachines made extensive use of their respective empire's factories.
Also, due to the usual effects of war on technological development,
the British and French both poured extensive amounts of money into
research and development of technology and weaponry.  Some of the
things that came out of the Steam War were the prototypes of
steam-powered cybernetics (steam-netics?), the first airships, and
other things.

December 20, 1861: SC secedes from the Union; Mississippi, Flordia,
Alabama, and Louisiana follow in the following weeks. (Virginia
[excluding W. Virginia], Arkansas, Tennessee, NC join at later dates)
\TODO{27 years}

February 8, 1860: The Confederate States of America are formed;
Jefferson Davis inaugurated 10 days later.

February 23, 1861: President-elect Abraham Lincoln assassinated in
Baltimore, Maryland.  Hannibal Hamlin becomes 16th President of the
United States.

April 12, 1861: American Civil War begins with Battle of Fort Sumter.

November 8, 1861: Beginning of the Trent Affair.

The USA never apologizes for boarding a neutral British warship.

January 2, 1862: Britain recognizes the CSA as an independant nation.
Becomes involved in the American Civil War, on the side of the CSA,
giving them the naval power to smash the US blockade.

(Various and sundry reasons for this.  Trent Affair was the
catalyst/excuse.  Canada, despite technically being part of the
British Empire, does NOT get involved.  Colonial Minister of Militia
and Defence, John A. Macdonald basically says "Are you bloody crazy?
Look at the border!" to the Brits, becoming a bit of a Canadian hero,
and the British agree that it would be pretty stupid to completely
antagonize the US.)

July 1, 1862: USA asks for peace talks.  CSA complies; general armistice.

September 13, 1962: American Civil War ends.  United States of America formally recognizes Confederate States of America as an independent nation.
[26 years]

May 3, 1863: Steam War ends, with Britian and France declaring armistice.
[25 years]

1870: \cTheif{} born. [18 years ago]

December 31, 1888: GAME TIME

*Follows actual historical timeline.
\end{document}
