

\documentclass[white]{airship}
\begin{document}

\name{\wNAPolitics{}} %% used as a label, doesn't typeset anything
State of the World: North America

The North American continent is the home of five distinct colonial
regions and nations: Canada, the United States of America (hereafter
referred to as the "USA"), the Confederate States of America
(hereafter referred to as the "CSA"), Texas, and Mexico.

History Lesson:

One of the interesting quirks of history followed the liberation of
the state of Texas from Mexico.  Originally, the theory was that
settlers from the United States came down into the region to help the
rebel insurgents successfully break from Mexico, form their own
independant nation, and then request statehood.  What actually
happened followed that original plan to a point.  Specifically, in
1845, the fledgling Texan government came to the conclusion that it
was strong enough to fight off any attempts by European powers to
reclaim that land by themselves and did not require the protection
statehood would offer.  Also, in another little quirk of history, the
United States did not press the issue much, to the point where every
subsequent time the issue of statehood was brought up, it was voted
down.  Instead, Texas remained as it was: it's own little
nation-state.

The division between the American States stems from the American Civil
War, wherein the southern states fought their northern breathren for
independence.  The war started in 1861 with the secession of South
Carolina, Mississippi, Flordia, Alabama, and Louisiana, later followed
by Virginia (excluding W. Virginia), Arkansas, Tennessee, and North
Carolina.  The northern states fought to keep the nation whole.

\TODO{is the trent affair explained in any white sheets? it needs to be}

However, using the Trent Affair as an excuse, Great Britain decided in
favor of economic need during the Steam War with France.  With the war
with France dragging into its fourth year, the British desperately
needed to keep their textile mills producing, thus requiring the
cotton and other agricultural products from the American South because
their colonies were too busy feeding the British warmachine to produce
the necessary amounts to keep Britain from going broke.  The Northern
blockade of the South threatened the British economy enough to warrent
action.  Therefore, the British Navy, still the most powerful navy in
the world, was sent to break the the blockade and succeeded.

With their blockade smashed and Great Britain's acknowledgement of the
Confederate States of America as an independant nation, the United
States half-heartedly continued the war for another seven months
before entering talks with the CSA for terms of surrender.  The
general concensus was to avoid antagonizing the British any more,
which worked, and resume normal trade relations, which happened.

On September 13, 1862, the American Civil War came to an end with the
recognition of the CSA by the USA as an independent nation and all
rights thereof.

Current Situation in the NA Continent:



\end{document}
