%%%%%
%%
%% This file creates the Item, ItemPacket, ItemFold, ItemEnvelope, and
%% ItemLabel datatypes, and creates macros for each.  These are for
%% various types of in-game items.
%%
%%%%%


%%%%%
%% Item macros are for normal item cards.
\DECLARESUBTYPE{Item}{TransElement}
\PRESETS{Item}{
  \FD\MYtext	{} %% longer text of item
  \FD\MYmark	{} %% possible contents of shaded ``mark'' on card
  \FD\MYbulky	{0} %% potential bulkiness
  \FD\MYcapacity{N/A} %% potential capacity
  }


%%%%%
%% \prop
%% \unstash
%% \bulky{<number>}
%% \contain{<number>}
%%
%% \prop inside an Item macro labels the card asr a prop.  \unstash
%% labels the card as unstashable.  \bulky{n} labels the card as
%% n-hands bulky.  \contain{n} labels the card with n-hands capacity.
\def\prop{%
  \append\MYmark{ ~PROP~ }}
\def\unstash{%
  \append\MYmark{ ~UNSTASHABLE~ }}
\def\bulky#1{%
  \s\MYbulky{#1}%
  \append\MYmark{\mbox{ ~\MYbulky-Hand~Bulky~ }}}
\def\contain#1{%
  \s\MYcapacity{#1}%
  \append\MYmark{\mbox{ ~\MYcapacity-Hand~Capacity~ }}}


%%%%%
%% ItemPacket macros are for item cards with an attached packet.
%% They are a subtype of Item.
\DECLARESUBTYPE{ItemPacket}{Item}
\PRESETS{ItemPacket}{
  \F\MYcontents
  }


%%%%%
%% ItemFold macros are for items represented by just a folded packet.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemFold}{ItemPacket}
\PRESETS{ItemFold}{
  \s\MYmark{}
  }


%%%%%
%% ItemEnvelope macros are for items represented by just an envelope.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemEnvelope}{ItemPacket}
\PRESETS{ItemEnvelope}{
  \s\MYmark{}
  }


%%%%%
%% ItemLabel macros are for small labels that would get used on
%% physreps, e.g. gun labels.  The ``mark'' is left blank, since
%% it isn't used for these.
\DECLARESUBTYPE{ItemLabel}{Item}
\PRESETS{ItemLabel}{
  \s\MYmark{}
  }


%%%%%
%% \icard[<extras>]{<name>}{<number>}{<text>}
%% \specialicard[<extras>]{<name>}{<number>}{<text>}{<mark>}
%% \itempacket[<extras>]{<name>}{<number>}{<text>}{<mark>}{<contents>}
%% \itemfold{<name>}{<number>}{<text>}{<contents>}
%% \itemenvelope{<name>}{<number>}{<text>}{<contents>}
%% \itemlabel{<name>}{<number>}{<text>}
%%
%% These are wrappers around \INSTANCE, useful for 1-shots.
%%
%% For \icard, \specialicard, and \itempacket, the optional <extras>
%% (in []'s) is for things like \unstash and \bulky{3}.  For example,
%% \icard[\prop\contain{2}]{..}{..}{..}{..} gives an item that has a
%% prop and 3-hands capacity.
%%
%% The last arg (#5) to \specialicard is for anything extra you may
%% want in the ``mark''
\newinstance{Item}{\icard[4][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}#1}
\newinstance{Item}{\specialicard[5][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}#1}
\newinstance{ItemPacket}{\itempacket[6][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}\s\MYcontents{#6}#1}
\newinstance{ItemFold}{\itemfold[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemEnvelope}{\itemenvelope[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemLabel}{\itemlabel[3]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\NEW{Item}{\iPreciseTools}{
  \s\MYname	{Precise Tools}
  \s\MYnumber	{792}
  \s\MYtext	{These tools are built for some specific, unknown task. Maybe they tune pianos, or repair grandfather clocks.}
  }

\NEW{Item}{\iDealerWatch}{
  \s\MYname	{A finely crafted pocket watch}
  \s\MYnumber	{46}
  \s\MYtext	{Engraved initials read ``E. B.''}
  }

% for pierre
\NEW{Item}{\iCyanide}{
  \s\MYname	{A small, empty vial.}
  \s\MYnumber	{2355}
  \s\MYtext	{This smells faintly of almonds\ldots{}}
  }

\NEW{Item}{\iParachute}{
  \s\MYname	{A parachute}
  \s\MYnumber	{234}
  \s\MYtext	{A small, self-contained parachute with a ripcord. If you stand by the {\em Envelope} of the ship,
you may make a ten-count action to don the parachute and jump. Go Not Here and see a GM.}
  }


\NEW{ItemPacket}{\iTestPacket}{
  \s\MYname	{Test Item}
  \s\MYnumber	{0000}
  \s\MYtext	{A Test Item with a big red button.  Open packet if
		you press the big red button.}
  \s\MYcontents	{The item beeps at you.}
  }

\NEW{ItemFold}{\iTestFold}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemEnvelope}{\iTestEnvelope}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemLabel}{\iTestLabel}{
  \s\MYname	{Test Gun Label}
  \s\MYnumber	{0000}
  \s\MYtext	{Disc gun, loadable to 20 shots.}
  }

\NEW{Item}{\iWhatzit}{
  \s\MYname	{Whatzit}
  \s\MYnumber	{12345}
  \s\MYtext	{If you press it, open packet a.  If you twirl it, open
		packet b.  If you pull it, open packet c.}
  \bulky	{1}
  \s\MYsigns	{\signstrip{a}{it goes ``beep.''}
		\signstrip{b}{it goes ``whoop.''}
		\signstrip{c}{it goes ``bang.''}
		}
  \s\MYabils	{\ability{Stop Crying}{By futzing with the Whatzit, you
		can make babies stop crying.}{I make the baby stop
		crying.}
		}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Item}{\iCane}{
  \s\MYname     {A Cane}
  \s\MYnumber   {62}
  \s\MYtext     {A lady or gentleman's finely crafted walking stick. {\bf Blunt}.}
  }
\NEW{Item}{\iSold}{
  \s\MYname  {Soldering Iron}
  \s\MYnumber {74}
  \s\MYtext  {A small, portable soldering iron.}
  }

\NEW{Item}{\iKnife}{
  \s\MYname	{A Knife}
  \s\MYnumber	{60}
  \s\MYtext	{{\bf Edged}}
  }

\NEW{Item}{\iJackKnife}{
  \s\MYname	{An Old Knife}
  \s\MYnumber	{66}
  \s\MYtext	{A jagged, slightly deformed knife that has seen much action. {\bf Edged}}
  }

\NEW{Item}{\iCeremonialSword}{
  \s\MYname	{A Ceremonial Sword}
  \s\MYnumber	{67}
  \s\MYtext	{A weapon not designed for combat. {\bf Edged}. Not bulky if worn at belt.}
  \bulky{1}
  }

\NEW{Item}{\iPipe}{
  \s\MYname	{A Lead Pipe}
  \s\MYnumber	{64}
  \s\MYtext	{A cylindrical piece of metal. {\bf +1 to CR}, {\bf Blunt}.}
  \bulky{1}
  }

\NEW{Item}{\iSword}{
  \s\MYname	{A Sword}
  \s\MYnumber	{61}
  \s\MYtext	{A fine military-grade weapon. {\bf Edged, +1 to CR}. Not bulky if worn at belt.}
  \bulky{1}
  }

\NEW{Item}{\iWeddingRing}{
  \s\MYname	{A Wedding Ring}
  \s\MYnumber	{38}
  \s\MYtext	{A very expensive diamond resting perfectly on a brilliantly gold wedding band.}
  }

\NEW{Item}{\iHugeOpiumShipment}{
  \s\MYname	{A Reinforced Crate}
  \s\MYnumber	{54}
  \s\MYtext	{Full to the brim with dark brown resin.}
  \bulky{6}
  \unstash
  }

\NEW{ItemFold}{\iOpium}{
  \s\MYname	{A pinch of opium}
  \s\MYnumber	{666}
  \s\MYtext	{You may smoke this opium at any time. If you do, open the item card.}
  \s\MYcontents	{{\em Wow,} this is concentrated. For the next two minutes, stumble around in an unresponsive, dream-like daze. You may not make attacks or defend yourself if attacked.}
  }

\NEW{ItemLabel}{\iSixShooter}{
  \s\MYname	{Revolver}
  \s\MYnumber	{367}
  \s\MYtext	{Maximum capacity of 6 bullets at any time. May not be reloaded unless you know otherwise.}
  }

\NEW{Item}{\iMoneyEnvelope}{
  \s\MYname	{A Sealed Envelope}
  \s\MYnumber	{55}
  \s\MYtext	{Stuffed with large denomination pound notes.}
  }

\NEW{Item}{\iSongBook}{
  \s\MYname	{Song Book}
  \s\MYnumber	{267}
  \s\MYtext	{An excellent collection of musical pieces for a soprano voice.}
  }

\NEW{Item}{\iRiggingKit}{
  \s\MYname	{Rigging Kit}
  \s\MYnumber	{11}
  \s\MYtext	{An industrial automated needler, strips of reinforced canvas, and coiled twine.}
  \bulky{1}
  }

\NEW{Item}{\iCanvasSheet}{
  \s\MYname	{Canvas Sheet}
  \s\MYnumber	{12}
  \s\MYtext	{A very durable sixty-four square feet of burlap.}
  \bulky{3}
  }

\NEW{Item}{\iMetalSheet}{
  \s\MYname	{Metal Sheet}
  \s\MYnumber	{13}
  \s\MYtext	{A thin, gleaming four square feet of metal.}
  \bulky{2}
  }

\NEW{Item}{\iToolkit}{
  \s\MYname	{Toolkit}
  \s\MYnumber	{14}
  \s\MYtext	{A rugged set of tools and instruments for the scientist or engineer.}
  \bulky{1}
  }

\NEW{Item}{\iHeatShield}{
  \s\MYname	{Heat Shield}
  \s\MYnumber	{15}
  \s\MYtext	{A thick, protective cylinder of insulating material.}
  \bulky{1}
  }

\NEW{Item}{\iWoodenTools}{
  \s\MYname	{Wooden Tools}
  \s\MYnumber	{16}
  \s\MYtext	{A collection of implements for cutting, attaching and unjamming wooden constructions.}
  \bulky{1}
  }

%%%%%%%%%%%%%%%%%%%%%%%%% Some more plot items

%There are multiple copies of this.

\NEW{Item}{\iCaptainKey}{
  \s\MYname	{A large well-weathered key.}
  \s\MYnumber	{30}
  \s\MYtext	{The inscription on it reads "Captain John Archer".}
  }

\NEW{Item}{\iCptBox}{
  \s\MYname     {A small storage box}
  \s\MYnumber   {785}
  \s\MYtext     {Locked. You may open this packet if you own {\bf item \#30}}
  \unstash
  \bulky{2}
 }

\NEW{Item}{\iBible}{
  \s\MYname	{Bible}
  \s\MYnumber	{777}
  \s\MYtext	{King James version.}
  }

\NEW{Item}{\iJackNecklace}{
  \s\MYname	{A necklace}
  \s\MYnumber	{33}
  \s\MYtext	{A series of masterfully cut, high-karat diamonds on a flawless golden chain. The most exotic, brilliant piece of jewelry you have ever laid your eyes on. Priceless. A small tag reads "Neptune's Tear".}
  \unstash
  }

\NEW{Item}{\iJackNecklaceAuth}{
  \s\MYname	{A piece of paper}
  \s\MYnumber	{34}
  \s\MYtext	{This is a certificate of authentication, attesting that the necklace included with it is the original and unmodified Neptune's Tear. It is adorned with several important-looking signatures.}
  }

\NEW{Item}{\iJackNecklaceKeyOne}{
  \s\MYname	{A small silver key}
  \s\MYnumber	{36}
  \s\MYtext	{}
  }

\NEW{Item}{\iJackNecklaceKeyTwo}{
  \s\MYname	{A small bronze key}
  \s\MYnumber	{37}
  \s\MYtext	{}
  }

\NEW{Item}{\iJackNecklaceCaseOne}{
  \s\MYname	{A reinforced crate}
  \s\MYnumber	{35-A}
  \s\MYtext	{This is the first locked layer of the reinforced crate. You may remove the next layer from within this envelope only if you open it with item \#36, or if you successfully pick the lock. Keep the envelopes you find inside close to this one. You can lock a layer by placing it back into its original enclosing envelope.}
  }

\NEW{Item}{\iJackNecklaceCaseTwo}{
  \s\MYname	{A reinforced crate}
  \s\MYnumber	{35-B}
  \s\MYtext	{This is the second locked layer of the reinforced crate. You may remove the next layer from within this envelope only if you open it with item \#30. The lock is impossible to pick.}
  }

\NEW{Item}{\iJackNecklaceCaseThree}{
  \s\MYname	{A reinforced crate}
  \s\MYnumber	{35-C}
  \s\MYtext	{This is the third locked layer of the reinforced crate. It is a combination lock. You may not open this envelope and extract the one within unless you know otherwise.}
  }

\NEW{Item}{\iJackNecklaceCaseFour}{
  \s\MYname	{A reinforced crate}
  \s\MYnumber	{35-D}
  \s\MYtext	{This is the fourth locked layer of the reinforced crate. You may remove the next layer from within this one only if you open it with item \#37, or if you successfully pick the lock. This is the last reinforced layer. Whatever the crate holds is inside this envelope.}
  }

\NEW{Item}{\iCaptainOtherSafe}{
  \s\MYname	{A heavy, combination safe}
  \s\MYnumber	{152}
  \s\MYtext	{You may not interact with this safe unless you know otherwise. If you open it, you may take or replace the items inside.}
  \bulky{3}
  }

\NEW{Item}{\iWhoreID}{
  \s\MYname	{A small badge}
  \s\MYnumber	{215}
  \s\MYtext	{This is a Scotland Yard Field Detective badge belonging to one "Emily Knight". It looks authentic.}
  }

\NEW{Item}{\iCaymanCharterFake}{
  \s\MYname	{A huge framed piece of parchment}
  \s\MYnumber	{167}
  \s\MYtext	{This seems to be a charter given by the British West India Steam Company that gives control of the Cayman Islands to the bearer. It is dated from 1634, and may no longer have any legal weight.}
  \bulky{2}
  \unstash
  }

\NEW{Item}{\iDeBeersStock}{
  \s\MYname	{A thick stack of sturdy paper}
  \s\MYnumber	{998}
  \s\MYtext	{{\bf Unstashable}. This entitles the bearer to 100,000 shares of stock in the De Beers Mining Company, established in Cape Town, South Africa in 1888. It is signed by {\em Cecil John Rhodes}.}
  }

\NEW{Item}{\iDeBeersDiamonds}{
  \s\MYname	{A small box filled with diamonds.}
  \s\MYnumber	{999}
  \s\MYtext	{{\bf Unstashable}.}

  }

\NEW{Item}{\iGeorgetownCharterFake}{
  \s\MYname	{A huge framed piece of parchment}
  \s\MYnumber	{169}
  \s\MYtext	{This seems to be a charter granted by the British West India Steam Company that allows the bearer to build and maintain a settlement on Grand Cayman called George Town. It is dated from 1646, and may no longer have any legal weight.}
  \bulky{2}
  \unstash
  }

\NEW{Item}{\iFireworks}{
  \s\MYname	{Fireworks}
  \s\MYnumber	{17}
  \s\MYtext	{Gunpowder rolled into a cardboard tube, with a long white wick. The front if capped off with a pointed head.}
  \bulky{1}
  }

\NEW{Item}{\iPlansAndTools}{
  \s\MYname	{Grimy tools wrapped in airship schemata}
  \s\MYnumber	{18}
  \s\MYtext	{This was obviously left over from the building of the ship. It seems completely useless at this point.}
  \bulky{1}
  }


%% Start - things needed for the Cowboy Fix Self Plot

\NEW{Item}{\iPropaneTorch}{
  \s\MYname	{Propane Torch}
  \s\MYnumber	{21}
  \s\MYtext     {A flame-spewing black metal cylinder. How this thing is powered by steam is beyond you.}
  }

\NEW{Item}{\iSolderingIron}{
  \s\MYname	{Soldering Iron}
  \s\MYnumber	{22}
  \s\MYtext	{The standard for dealing with wires.}
  }

\NEW{Item}{\iSpoolCopper}{
  \s\MYname	{Spool of Copper Wire}
  \s\MYnumber	{23}
  \s\MYtext	{A tightly bound coil.}
  }

\NEW{Item}{\iStandardPiston}{
  \s\MYname	{Standard Piston}
  \s\MYnumber	{24}
  \s\MYtext	{This looks like it could belong inside the airship{\ldots}. Hopefully it's not terribly important.}
  }

%% misc. plots

\NEW{Item}{\iOpiumPlotNote}{
  \s\MYname    {a handwritten note}
  \s\MYnumber  {734}
  \s\MYtext    {This is a barely legible set of instructions on how to get into some sort of secret hiding spot. While carrying this item, you may lift up {\em Sign \#822} and read the sign under it.}
  }
