\documentclass[green]{airship}
\begin{document}
\name{\gCowboyRepair{}}

This greensheet details how to repair your legs.  

Your legs are not top-of-the-line medical prosthetics, and as such do not require being in a hospital to repair.  This is a good thing, as your legs have been damaged in three places.  At the start of game, {\em you must limp or walk stop-step, and your CR is reduced to 1}.

You have three repair packets, which may be opened once you complete the given repair task.  These tasks must be perfomed in order, and you may have other individuals complete individual steps.

The right calf has only superficial damage.

\begin{enum}[Right Calf]
  \item Find a {\bf Propane torch}.
  \item Find a {\bf Metal Sheet}.
  \item Spend two minutes working on the leg and destroy these two items.
\end{enum}

\begin{enum}[Left Ankle]
  \item Find a {\bf Toolkit}.
  \item Find a single {\bf Lead Pipe}.
  \item Find a {\bf Rigging Kit}
  \item Find a {\bf Metal Sheet}
  \item Spend five minutes working on the leg.  Afterwards, destroy these items. This requires the presence of somebody with the ``Repair'' ability.
\end{enum}

\begin{enum}[Left Knee]
  \item Find a {\bf Soldering Iron}.
  \item Find a {\bf spool of copper wire}.
  \item Find a {\bf Standard Piston}
  \item Find a {\bf Rigging Kit}
  \item Find a {\bf Toolkit}.
  \item Find two {\bf Lead Pipes}.
  \item Spend five minutes working on the leg.  Afterwords, destroy these items. This requires the presence of somebody with the ``Repair'' ability.
\end{enum}


\end{document}
