\documentclass[green]{airship}
\begin{document}
\name{\gCrawlspace{}}

To learn how to crawl around the inside of the {\em HMS Dauntless}, read this greensheet. If you have a $\phi$ stat, you are small, slender or athletic enough to crawl around more easily than normal.

There are four Crawlspace locations on the airship, and moving between them is generally one-way.

\begin{enum}[Locations]
  \item {\bf Crawlspace Alpha} in 38-3 leads to {\bf Crawlspace Beta} in 36-3.
  \item {\bf Crawlspace Beta} in 36-3 leads to {\bf Crawlspace Gamma} in 26-3.
  \item {\bf Crawlspace Gamma} in 26-3 leads to {\bf Crawlspace Delta} in 24-3.
  \item {\bf Crawlspace Delta} in 24-3 leads to {\bf Crawlspace Alpha} in 38-3.
\end{enum}

\begin{enum}[Departing from this Crawlspace]
  \item Place both hands on the Crawlspace sign and count to ten. This is an interruptable action.
  \item Go Not Here. Place your hands above your head or put on a white headband. While Not Here, you can still hear and see game action around you, and you may still speak. Your voice sounds like it is coming out of the walls.
  \item Start walking to the location of the next Crawlspace. If you do not have a $\phi$ stat, you must walk heel-toe, and you become {\bf Winded} (you can only walk heel-toe and your CR is lowered by one) for a minute after you arrive at your destination. If your $\phi$ is one, you may walk normally and suffer no ill effects from using a Crawlspace. If your $\phi$ is two, you may run at a safe speed between crawlspaces, and suffer no ill effects.
  \item At no point may you stop moving at least at heel-toe speed to the next Crawlspace.
\end{enum}

\noindent {\bf Items}\\ \indent Along the way in your explorations of the crawlspaces of the {\it HMS Dauntless}, it is possible you might run into interesting items. When you arrive at a Crawlspace you may take a single item out of an envelope marked {\bf Items} attached to the back of the {\bf Open} sign. You may not take another item out of any Crawlspace unless you return to game, and then re-enter the crawlspace system. If your $\phi$ is 2, you may take two items.

\begin{enum}[Arriving at a Crawlspace]
  \item If the Crawlspace if marked as {\bf Open}, come back into game upon arriving at the Crawlspace at tagging the sign. You may not automatically proceed to the next Crawlspace without climbing back in.
  \item If the Crawlspace if marked as {\bf Closed}, then you are in trouble. The end of this Crawlspace is sealed with a {\bf Metal Sheet}. If you have a {\bf Toolkit}, you may follow the instructions on the front of the Crawlspace sign to remove {\bf Metal Sheet} and exit the Crawlspace. 
  \item If you are trapped at a {\bf Closed} Crawlspace, and it suddenly becomes {\bf Open}, you tumble out of the Crawlspace and back into game.
  \item Alternately, if the Crawlspace is {\bf Closed}, you may turn around and return to the Crawlspace you came from.
  \item Note that it is possible to get stuck bouncing back and forth between two {\bf Closed} Crawlspaces with no {\bf Toolkit}. You are then at the mercy of the ship's other passengers.
\end{enum}

\end{document}
