%%%%%
%%
%% Greensheets live in this directory.  This file doubles as a
%% latex'able example greensheet.
%%
%% Greensheet macros (in ../Lists/green-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given greensheet, which will generate
%% the greensheet's name as specified in green-LIST.tex.  However, you
%% can also just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[green]{airship}
\begin{document}

\name{\gGrowup{}}

This Greensheet describes how you can collect data to develop a personality of your very own. 

You may complete the following four steps in any order, and you may interleave them. Keep track of the steps separately, however. The only people that may be used for this mechanic are ones with badge numbers \#532, \#537, \#239, and \#337.

\begin{itemize}
  \item Get three people to tell you a story about their past. The story must be at least two minutes long. If it is shorter than that, keep asking questions until it has been the full two minutes. Write down who told you the story, and what it was about. (The list is not in-game.) Circle which story was most interesting, and give the list to a GM. 
  \item Get three people to demonstrate an ability that you do not have, and give you an in-game, in-character explanation about how it works. They must be three different abilities. The explanation should last at least a minute. If it doesn't, keep asking questions until it has been a minute. Write down who showed you what ability, circle which one you liked best, and give it to a GM.
  \item Get three people to tell you a non-trivial (if in doubt, ask a GM)  secret. If you as a player don't believe them, it doesn't count. Write down who told you what secret, circle which one you liked best and give the list to a GM.
  \item Get three people to tell you what they think is the most important personality trait for a person to have, and why. Write down who told you what, circle which one you most agree with and give the list to a GM.
\end{itemize}

Once you have completed these tasks, you will begin incorporating the collected information into your new personality. It will take the GMs a few minutes to get back to you, but we will shortly hand you a description of your new behaviors.

\end{document}
