\documentclass[green]{airship}
\begin{document}
\name{\gRepair{}}

This greensheet details how to repair the {\it HMS Dauntless}. If you are reading this greensheet, then you have some knowledge of how carry out emergency inflight repairs.

This airship is kept in flight by five critical {\it Airship Stations}. Occasionally these stations become broken through normal wear and tear, but, much more commonly, they can be sabotaged into not working properly. The fate of the {\it Dauntless} depends on how many stations are operational at the end of game. If all stations are operational, the airship comes to a perfect landing. If three or four stations are operational, the airship lands bumpily and shamefully, and safely. If one or two stations are operational, the airship issues mayday warnings, and plummets into the nearest mountain or tall building. If no stations are active at the end of game, the airship explodes with a brilliant fireball.

However, it as a bad idea to leave the repair of all stations until five minutes before landing. Letting stations stay broken for long stretches of time can have disastrous effects{\ldots}

Following this is a breakdown of how to fix each of the five {\it Airship Stations}:

\begin{enum}[Envelope Tie]
  \item The envelope tie is the only station that one does not need to be a trained engineer to repair.
  \item Find a {\bf Canvas Sheet}.
  \item Find a {\bf Rigging Kit}.
  \item Spend two minutes in front of the station and destroy these two items.
\end{enum}

\begin{enum}[Steering Wheel]
  \item Find up to three willing people. They need not have any knowledge of airship repair.
  \item Each person participating must have a {\bf Wooden Tools}, (yourself included).
  \item Find a single {\bf Lead Pipe}.
  \item Each person must stand within ZoC of the station. It requires eight minutes, divided by the number of workers, to repair. Thus, you can repair it by yourself in eight minutes, and in two minutes with three helpers (the maximum).
\end{enum}

\begin{enum}[Boiler]
  \item Find a {\bf Lead Pipe}.
  \item Find a {\bf Toolkit}.
  \item Find a {\bf Metal Sheet}.
  \item Spend three minutes within ZoC of the station and destroy these three items.
\end{enum}

\begin{enum}[Engine]
  \item Find two {\bf Metal Sheets}.
  \item Find a {\bf Heat Shield}.
  \item Find another willing person. They don't have to know anything about airship repair.
  \item Both of you must spend two minutes with your hands firmly on the sign. Destroy the three items.
\end{enum}

\begin{enum}[Repulsorlift Stabilizer]
  \item Find a {\bf Heat Shield}.
  \item Find a {\bf Canvas Sheet}.
  \item Find a {\bf Toolkit}.
  \item Find a {\bf Rigging Kit}.
  \item Spend three minutes within ZoC of the station and destroy these four items.
\end{enum}


\end{document}
