\documentclass[green]{airship}
\begin{document}
\name{\gSabotage{}}

This greensheet details how to sabotage, juryrig and destroy the {\it HMS Dauntless}. If you are reading this greensheet, then you have some knowledge of how carry out inflight sabotage.

This airship is kept in flight by five critical {\it Airship Stations}. Occasionally these stations become broken through normal wear and tear, but, much more commonly, they can be sabotaged into not working properly. The fate of the {\it Dauntless} depends on how many stations are operational at the end of game. If all stations are operational, the airship comes to a perfect landing. If three or four stations are operational, the airship lands bumpily and shamefully, and safely. If one or two stations are operational, the airship issues mayday warnings, and plummets into the nearest mountain or tall building. If no stations are active at the end of game, the airship explodes with a brilliant fireball.

However, it as a bad idea to try to sabotage everything five minutes before landing, as any ship worth its salt has a crew of engineers able to fix it{\ldots}

Following this is a breakdown of how to sabotage each of the five {\it Airship Stations}:

\begin{enum}[Envelope Tie]
  \item The envelope tie is the only station that can be sabotaged by anyone.
  \item Find a {\bf Edged} weapon.
  \item Spend two minutes in front of the station.
\end{enum}

\begin{enum}[Steering Wheel]
  \item Find a single {\bf Toolkit}.
  \item Stand within ZoC of the station. It requires three minutes in front of the station.  Once completed, destroy the {\bf Toolkit}.
\end{enum}

\begin{enum}[Boiler]
  \item Find a {\bf Lead Pipe}, or a {\bf Sword}.
  \item Spend one minute attacking the sign with this weapon.
  \item Find a {\bf Metal Sheet}.
  \item Spend one minute within ZoC of the station and destroy the {\bf Metal Sheet}.
\end{enum}

(It is possible to disable the Engine in two ways)
\begin{enum}[Engine]
  \item Hit the Engine with two {\bf CR} 4 {\bf Wound} attacks.
  \item OR
  \item Find a piece of {\bf Fireworks}, and spend two minutes within ZoC of the station with it.
\end{enum}

\begin{enum}[Repulsorlift Stabilizer]
  \item Find a {\bf Heat Shield}, to protect yourself while you work.
  \item Find a {\bf Propane Torch}.
  \item Spend two minutes in front of the Repulsorlift Stabilizer and destroy the {\bf Propane Torch}.
\end{enum}


\end{document}
