\documentclass[green]{airship}
\begin{document}
\name{\gWolf{}}
% Grace points earned through good deeds, lost through bad deeds, can be applied to others to work on converting them, or to self to suppress werewolf. Vaguely worked off of Seven Heavenly Virtues/Deadly Sins.

This greensheet details the workings of the curse that has been inflicted upon you. A raging creature of hatred, violence and sin has been awoken deep inside you, and every moral misstep you make feeds it. Likewise, pious actions will fend off the beast - or, if you choose, will set an example for others.

This balance is represented in game with the {\bf Grace} and {\bf Sin} stats. They can be modified by events that take place in game. Be your own harshest critic as to when the following apply.

\begin{enum}[Grace]

\item Publically lead others in prayer during a time of danger - 1 point. (You may only do this once per game, and one additional time for any major cataclysms that occur during game - e.g. The captain dies and the ship begins to plummet)

\item Talking down an argument to at least a grudging compromise - 1 point.

\item Stopping a violent conflict - 2 points.

\item Directly saving a life through your own action - 3 points.

\item Being injured while pursuing these goals - 1 point in addition to any other rewards.

\item Dying as a result of pursuing these goals - 3 points in additon to any other rewards, including being injured.
\end{enum}

\begin{enum}[Sin]

\item Viewing public, obvious displays of anger (shouting, throwing things, swearing) - 1 point for each instance. 

\item Observing any of the traditional sins - stealing, violence, promiscuity, lying, etc. - 1 point.\footnote{Unconscious, Wounded or Dead bodies count as observing violence.}

\item Taking an item without the owner's permission - 1 point, 3 points if it is an expensive item, such as jewelry.

\item Not telling the truth, or telling the truth in a deliberately misleading fashion - 1 point.

\item Directing violence towards another character - 2 points per incident.

\item Killing someone - 5 points.
\end{enum}

\begin{enum}[Effects of Grace and Sin]

\item You can use Grace points to power your Preach ability. One point allows one activation of the power. People without a $\chi$ stat are either already Christian or inconvertible. If you use this ability on someone without a $\chi$ stat, Grace is still expended. Grace cannot go below zero.

\item If your Sin ever increases to or above 4, open your W packet. If your Sin is above 4 and increases, open your W packet. You may have to open this packet multiple times during game. Follow its instructions each time. 
\end{enum}

\end{document}
